# Grain {#cha:grain}



```{r grain-setup, message=FALSE, warning=FALSE, echo=FALSE}
source('_setup.R')
```


## Grain number {#sec:grain-number}

Grain number is correlated with stem [ref] and/or spike [@SlaferGeneticimprovementeffectspreanthesis1990;@GonzalezPhotoperiodstemelongation2005] dry weight at anthesis.

The number of grains per plant ($N_{g}$) is determined by the `Stem` and `Spike` total biomass at `Flowering` (including `Live` and `Dead`).
$$
N_{g}=R_{g}(W_{stem} + W_{spike})
$$
where $W_{stem}$ and $W_{spike}$ are the stem and spkie total biomass at flowering, respectively. R_{g} is the grain number per gram stem and spike, with default value at `r get_fixed_value(g_pmf, 'Wheat.Grain.NumberFunction.GrainNumber.GrainsPerGramOfStem')` grain g<sup>-1</sup>.




## Supply {#sec:grain-supply}

No biomass supply is considered in the `Grain` organ (Fig. \@ref(fig:grain-supply)).


<div class="fig-output">
```{r grain-supply, fig.asp = 0.5, fig.cap='Biomass supply from grain'}
y_cols <- c('Wheat.Grain.DMSupply.Fixation',
            'Wheat.Grain.DMSupply.Retranslocation',
            'Wheat.Grain.DMSupply.Reallocation')

plot_report(g_report, g_xvar2, y_cols, x_lab = g_xlab, 
            y_lab = expression(atop('Biomass supply', '(g biomass '~m^-2~' ground '~d^-1~')')), 
            ncol = 3)

```
</div>


## Demand {#sec:grain-demand}
The grain demand is seperated into two periods (i.e. from `Flowering` to `StartGrainFill` and from `StartGrainFill` to `EndGrainFill`). 


<div class="fig-output">
```{r grain-demand, fig.asp = 1, fig.cap='Biomass demand by grain'}
y_cols <- c('Wheat.Grain.DMDemand.Structural', 
            'Wheat.Grain.DMDemand.Metabolic', 
            'Wheat.Grain.DMDemand.Storage')
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Biomass demand (g biomass '~m^-2~' ground '~d^-1~')'), 
            ncol = 3)

```
</div>

## Biomass dynamic {#sec:grain-dynamic}

`Grain` only considers the `Live` conponent, No `Dead` component.



<div class="fig-output">
```{r grain-allocated, fig.asp = 1, fig.cap='Actual allocated biomass for grain'}
y_cols <- c('Wheat.Grain.Allocated.StructuralWt',
            'Wheat.Grain.Allocated.MetabolicWt',
            'Wheat.Grain.Allocated.StorageWt')
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Allocated biomass (g biomass '~m^-2~' ground '~d^-1~')'),
            ncol = 3)
```
</div>




<div class="fig-output">
```{r grain-weight, fig.asp = 1, fig.cap='Dynamic of grain biomass (Total)'}
y_cols <- c('Wheat.GrainWt')

plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Biomass (g biomass '~m^-2~' ground '~d^-1~')'))

```
</div>





<div class="fig-output">
```{r grain-live, fig.asp = 1, fig.cap='Dynamic of grain biomass (Live component)'}
y_cols <- c('Wheat.Grain.Live.StructuralWt',
            'Wheat.Grain.Live.MetabolicWt',
            'Wheat.Grain.Live.StorageWt')

plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Biomass (g biomass '~m^-2~' ground '~d^-1~')'),
            ncol = 3)

```
</div>


<div class="fig-output">
```{r grain-dead, fig.asp = 0.5, fig.cap='Dynamic of grain biomass (Dead component)'}
y_cols <- c('Wheat.Grain.Dead.StructuralWt',
            'Wheat.Grain.Dead.MetabolicWt',
            'Wheat.Grain.Dead.StorageWt')


plot_report(g_report, g_xvar2, y_cols, x_lab = g_xlab, 
            y_lab = expression(atop('Biomass','(g biomass '~m^-2~' ground '~d^-1~')')),
            ncol = 3)

```
</div>




### Yield

The total grain weight at harvest can be considered as the final yield without moisture content in the grain. The normal range of moisture content in the grain is 10-15% with 12% as standard

<div class="fig-output">
```{r grain-yield, fig.asp = 0.5, fig.cap='Final yield with different moisture content.'}

final_yield <- max(g_report$Wheat.GrainWt)
mos <- seq(0, 15)
data_frame(Moisture = mos,
           yield = (1 + mos / 100) * final_yield / 100) %>% 
    ggplot() +
    geom_bar(aes(Moisture, yield), stat = 'identity', position = "dodge") +
    xlab('Moisture content (%)') + 
    ylab(expression('Yield (t'~ha^-1~')')) +
    theme_bw()
 
```
</div>
