---
title: "Documentation of APSIM-Wheat"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [citation.bib]
biblio-style: citation.csl
link-citations: yes
github-repo: byzheng/APSIM-Wheat
description: "Documentation of APSIM-Wheat"

---


# Introduction {#cha:intro}

This documentation is based on the current version of [APSIM-Wheat module](https://github.com/APSIMInitiative/ApsimX/tree/d9717df5ef24f6d3f1eb4c301726c213960017bb) with a few modifications in the next generation updated on 17-August-2017.

A simulation is setup to demo the relationship among traits based on the cv. Hartog with high nitrogen and irrigation management under 15TraitMod experiment. The values in the figures below could be variable in other environments.


```{r index-setup, message=FALSE, warning=FALSE, echo=FALSE}
source('_setup.R')
```



This is only a documentation for Wheat model in [next generation of APSIM](https://github.com/APSIMInitiative/ApsimX) with our own understanding.

The main contents include 

- Detail description of science parts of APSIM-Wheat model
- Figures of default parameters
- Figures of general outputs


## Contributors {#sec:intro-contribution}
 * [Bangyou Zheng](https://www.bangyou.me) <bangyou.zheng@csiro.au>
 * [Karine Chenu](https://qaafi.uq.edu.au/profile/18/karine-chenu) <karine.chenu@uq.edu.au>
 * [Scott Chapman](http://people.csiro.au/C/S/Scott-Chapman) <scott.chapman@csiro.au>
 * [Enli Wang](http://people.csiro.au/W/E/Enli-Wang) <enli.wang@csiro.au>
 * Fernanda Dreccer <Fernanda.Dreccer@csiro.au>



## Conventions {#sec:intro-convention}

### Figures

Figures in the documentation are classified into two categories with different backgrounds, i.e. `Input` and `Output`. `Input` figures show default parameter values (not genotypic values) or dynamic parameter values (depending on the other status variables) in the APSIM Next Gen model. `Output` figures show reportable variables in the in the APSIM Next Gen model. The `Input` and `Output` variable names only show the last section (separated by full stop) or specified names to save spaces in the figures.

Most of figures use two time serial variables, i.e. `Stage` and `Accumulated thermal time since sowing`. However, only `Stage` is used if all values are constant (e.g. Fig. \@ref(fig:root-supply)), or stage based input variables.

The key stages are displayed in all figures (Section \@ref(sec:phe-stage-period)) including `G` for stage 2 `Germination`, `T` for stage 4 `Terminal Spikelet`, `F` for stage 6 `Flowering`, `E` for stage 8 `End of Grain Filling`.



## How to contribute {#sec:intro-own-contribution}

This documentation is wrote by [RMarkdown](rmarkdown.rstudio.com) and [bookdown](bookdown.org). I suggest you firstly to read the introduction about [RMarkdown](rmarkdown.rstudio.com) and [bookdown](bookdown.org), then fork this repository into your github account. Feel free to submit a pull request. 


The new document can be easily generated for any other simulations using following steps.

* Install the required software including [R](https://cran.r-project.org/), [RStudio](https://www.rstudio.com/), [Bookdown](https://bookdown.org/yihui/bookdown) and other depended packages.
* Fork or download all source codes from [git repository](https://github.com/byzheng/APSIM-Wheat-Doc).
* Replace your own simulation.apsimx under simulation subfolder. Your apsimx file should only have `ONE` simulation and include all report variables used in the report, which can be found in the report replacement of the existing apsimx file.
* Click `Build book` in the RStudio interface.

### Retrieve fixed value

`get_fixed_value` function is used to retrieve `FixedValue` in APSIM Next Gen. The `path` argument is used to specify the full path to the node with class `FixedValue` using APSIM format which connects the names of all predecessors started from `Wheat`. For example, the code below is used to obtain value for `GrainsPerGramOfStem` with value `r get_fixed_value(g_pmf, path = 'Wheat.Grain.NumberFunction.GrainNumber.GrainsPerGramOfStem')`.

```{r intro-get-fixed-value, echo=TRUE, eval=FALSE}
get_fixed_value(g_pmf, 
    path = 'Wheat.Grain.NumberFunction.GrainNumber.GrainsPerGramOfStem')
```


### Add new figure

Figures are classified into `Input` and `Output` categories (Section \@ref(sec:intro-convention)). `div` tags in html are used to specify the category. 


````markdown
<div class="fig-input">
`r ''````{r chunk-label, fig.asp=1, fig.cap='A figure caption.'}
# add you codes here
```
</div>

<div class="fig-output">
`r ''````{r chunk-label, fig.asp=1, fig.cap='A figure caption.'}
# add you codes here
```
</div>
````

Two variables are exposed to global environment (`.GlobalEnv` in R), i.e. `g_pmf` for an `xml` object of the simulation file `_simulation/simulation.apsimx`, and `g_report` for a `data.frame` of the simulation output file. Variables `g_pmf` and `g_report` can be used in any places of the documentation. 

A few `helper` functions are designed to plot figures, i.e. `plot_xypair` and `plot_report`. 

`plot_xypair` is used to plot the `XYPairs` function in APSIM Next Gen. The `path` argument is used to specify the full path of a node with child `XYPairs` using APSIM format which connects the names of all predecessors started from `Wheat` (e.g. `Wheat.Leaf.CohortParameters.MaxArea.AgeFactor`). `g_xlab` and `y_lab` can be used to specify the X and Y labels. 

```{r intro-example-plot-xypair, echo=TRUE, eval=FALSE}
path <- 'Wheat.Leaf.CohortParameters.MaxArea.AgeFactor'
plot_xypair(g_pmf, path,
            x_lab'Growthing stage', 
            y_lab = 'Multiplier of maximum leaf area')
```

`plot_report` is used to plot outputs of APSIM Next Gen for a single and multiple variables. Two types of X variables are predefined in the global environment (i.e. `g_xvar` for thermal time and stage; `g_xvar2` for stage only). `X` label is also defined in the global environment. These variables can be overwrote when the `plot_report` is called, but DO NOT add into global environment as other chunks use the default values. 

```{r intro-xvar, echo=TRUE, eval=FALSE}
g_xvar <- c('Wheat.Phenology.Stage',
           'Wheat.Phenology.AccumulateThermalTime')
g_xvar2 <- c('Wheat.Phenology.Stage')
g_xlab <- 'Accumulated thermal time or stage'
```

The argument `y_cols` is used to specify one and multiple variables in the APSIM report using `plot_report` function. Y label `y_lab` should be specified for each figure.

```{r intro-example-plot-report, echo=TRUE, eval=FALSE}
y_cols <- c('Wheat.Leaf.DMSupply.Fixation',
            'Wheat.Leaf.DMSupply.Retranslocation',
            'Wheat.Leaf.DMSupply.Reallocation')
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = 'Demand (g/d)', ncol = 3)
```





## Software information {#sec:intro-software}

The R session information when compiling this book is shown below:

```{r session}
sessionInfo()
```

