## Nitrogen {#sec:leaf-nigrogen}


### Functional nitrogen

Ratio of leaf functional nitrogen ($f_{N,\,leaf}$) quantifys the nitrogen stress status of the plant and represents the concentration of metabolic N relative the maximum potentil metabolic N content of the leaf.


$$
f_{N,\,photo}=R_{N,\,photo}\frac{C_{N}-C_{N,\,min}}{C_{N,\,crit}-C_{N,\,min}}
$$

where $C_{N}$ is the nitrogen concentration of `Leaf` parts; $R_{N,\,expan}$ is multiplier for nitrogen deficit effect on phenology which is specified by `N_fact_photo` in the wheat.xml and default value is 1.5.



<div class="fig-input">
```{r leaf-nconc, fig.asp = 1, fig.cap='Actual allocated biomass for leaf'}
y_cols <- c('Wheat.Leaf.CohortParameters.MinimumNConc',
'Wheat.Leaf.CohortParameters.CriticalNConc',
'Wheat.Leaf.CohortParameters.MaximumNConc')
y_labels <- c('Minimum', 'Critical', 'Maximum')
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = 'Nitrogen concentration (g/m2)', ncol = 3,
            y_labels = y_labels)

```
</div>


<div class="fig-output">
```{r leaf-nitrogen-functional-n, fig.cap='Ratio of functional nitrogen'}
y_cols <- c('Wheat.Leaf.Fn')
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, y_lab = 'Ratio of functional nitrogen')

```
</div>




<div class="fig-output">
```{r leaf-sln, fig.asp = 1, fig.cap='Specific leaf nitrogen'}
y_cols <- c('Wheat.Leaf.SpecificLeafNitrogen')

plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = 'Specific leaf nitrogen (g/m2)', ncol = 3)
```
</div>
