## Nitrogen {#sec:leaf-nigrogen}

### Functional nitrogen

Ratio of leaf functional nitrogen ($f_{N,\,leaf}$) quantifys the nitrogen stress status of the plant and represents the concentration of metabolic N relative the maximum potentil metabolic N content of the leaf.


$$
f_{N,\,leaf}=C_{leaf} / (\frac{C_{critical,\,leaf}-C_{min,\,leaf} \times S_{leaf}}{1-S_{leaf}})
$$

where $C_{N}$ is the nitrogen concentration of `Leaf` parts; $R_{N,\,expan}$ is multiplier for nitrogen deficit effect on phenology which is specified by `N_fact_photo` in the wheat.xml and default value is 1.5.

double functionalNConc = (CohortParameters.CriticalNConc.Value() -
                                          CohortParameters.MinimumNConc.Value() * CohortParameters.StructuralFraction.Value()) *
                                         (1 / (1 - CohortParameters.StructuralFraction.Value()));
                


<div class="fig-input">
```{r leaf-nconc, fig.asp = 1, fig.cap='Minimum, critical and maximum nitrogen concentration in leaf.'}
y_cols <- c('Wheat.Leaf.CohortParameters.MinimumNConc',
'Wheat.Leaf.CohortParameters.CriticalNConc',
'Wheat.Leaf.CohortParameters.MaximumNConc')
y_labels <- c('Minimum', 'Critical', 'Maximum')
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
        y_lab = expression('Nitrogen concentration (g N'~g^-1~' leaf)'), 
        ncol = 3,
        y_labels = y_labels)

```
</div>


<div class="fig-output">
```{r leaf-nitrogen-functional-n, fig.asp=0.5, fig.cap='Ratio of functional nitrogen'}
y_cols <- c('Wheat.Leaf.Fn')
plot_report(g_report, g_xvar2, y_cols, x_lab = g_xlab2, 
            y_lab = 'Ratio of functional nitrogen[-]')

```
</div>





### Nitrogen demand


<div class="fig-output">
```{r leaf-nitrogen-demand, fig.asp=1, fig.cap='Nitrogen demand of leaf.'}
y_cols <- c('Wheat.Leaf.NDemand.Total',
            'Wheat.Leaf.NDemand.Structural', 
            'Wheat.Leaf.NDemand.Metabolic', 
            'Wheat.Leaf.NDemand.Storage')
plot_report(g_report, g_xvar, 
            y_cols, x_lab = g_xlab, 
            y_lab = expression('Nitrogen demand (g N ' ~m^-2~'ground)'),
            ncol = 4)
```
</div>




### Nitrogen amount

<div class="fig-output">
```{r leaf-nitrogen-content, fig.asp=1, fig.cap='Nitrogen contents in live and dead pools of leaf.'}
y_cols <- c('Wheat.Leaf.Live.N', 'Wheat.Leaf.Dead.N')
plot_report(g_report, g_xvar, 
            y_cols, x_lab = g_xlab, 
            y_labels = c('Live', "Dead"),
            y_lab = expression('Nitrogen content (g N ' ~m^-2~'ground)'),
            ncol = 2)
```
</div>


<div class="fig-output">
```{r leaf-nitrogen-content-component-live, fig.asp=1, fig.cap='Nitrogen contents of three components in live pool of leaf.'}
y_cols <- c("Wheat.Leaf.Live.N", 
            'Wheat.Leaf.Live.StructuralN', 
            'Wheat.Leaf.Live.MetabolicN',
            'Wheat.Leaf.Live.StorageN')
plot_report(g_report, g_xvar, 
            y_cols, x_lab = g_xlab, 
            y_labels = c("Total", 'Structural', "Metabolic", 'Storage'),
            ncol = 4,
            y_lab = expression('Nitrogen content (g N ' ~m^-2~'ground)'))
```
</div>



<div class="fig-output">
```{r leaf-nitrogen-content-component-dead, fig.asp=1, fig.cap='Nitrogen contents of three components in dead pool of leaf.'}
y_cols <- c("Wheat.Leaf.Dead.N",
            'Wheat.Leaf.Dead.StructuralN', 
            'Wheat.Leaf.Dead.MetabolicN',
            'Wheat.Leaf.Dead.StorageN')
plot_report(g_report, g_xvar, 
            y_cols, x_lab = g_xlab, 
            y_labels = c("Total", 'Structural', "Metabolic", 'Storage'),
            ncol = 4,
            y_lab = expression('Nitrogen content (g N ' ~m^-2~'ground)'))
```
</div>


<div class="fig-output">
```{r leaf-nitrogen-concentration, fig.asp=0.5, fig.cap='Nitrogen concentration in live and dead pools of leaf.'}
y_cols <- c('Wheat.Leaf.Live.NConc', 'Wheat.Leaf.Dead.NConc')
plot_report(g_report, g_xvar, 
            y_cols, x_lab = g_xlab, 
            y_labels = c('Live', "Dead"),
            y_lab = expression('Nitrogen concentration (g N ' ~g^-1~'leaf)'),
            ncol = 2)
```
</div>


<div class="fig-output">
```{r leaf-nitrogen-concentration-component-live, fig.asp=1, fig.cap='Nitrogen concentration of three components in live pool of leaf.'}
y_cols <- c('Wheat.Leaf.Live.NConc',
            'Wheat.Leaf.Live.StructuralNConc', 
            'Wheat.Leaf.Live.MetabolicNConc',
            'Wheat.Leaf.Live.StorageNConc')
plot_report(g_report, g_xvar, 
            y_cols, x_lab = g_xlab, 
            y_labels = c('Leaf', 'Structural', "Metabolic", 'Storage'),
            ncol = 4,
            y_lab = expression('Nitrogen concentration (g N ' ~g^-1~'leaf)'))
```
</div>




<div class="fig-output">
```{r leaf-nitrogen-concentration-component-dead, fig.asp=1, fig.cap='Nitrogen concentration of three components in dead pool of leaf.'}
y_cols <- c('Wheat.Leaf.Dead.NConc',
            'Wheat.Leaf.Dead.StructuralNConc', 
            'Wheat.Leaf.Dead.MetabolicNConc',
            'Wheat.Leaf.Dead.StorageNConc')
plot_report(g_report, g_xvar, 
            y_cols, x_lab = g_xlab, 
            y_labels = c('Leaf', 'Structural', "Metabolic", 'Storage'),
            ncol = 4,
            y_lab = expression('Nitrogen concentration (g N ' ~g^-1~'leaf)'))
```
</div>





<div class="fig-output">
```{r leaf-sln, fig.asp = 1, fig.cap='Specific leaf nitrogen'}
y_cols <- c('Wheat.Leaf.SpecificLeafNitrogen')

plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Specific leaf nitrogen (g N'~m^-2~' leaf)'),
                               ncol = 3)
```
</div>
