# Root {#cha:root}


```{r root-setup, message=FALSE, warning=FALSE, echo=FALSE}
source('_setup.R')
```


Only `Structural` is considered in the three components of biomass for `Root`. The biomass allocation depending on the fraction of daily fixation (i.e. photosynthesis).



## Root Growth {#sec:root-growth}

Roots grow downwards through the soil profile, with initial depth determined by sowng depth and the growth rate determined by RootFrontVelocity. 

The RootFrontVelocity is modified by multiplying it by the soil's XF value; which represents any resistance posed by the soil to root extension. 
Root depth is also constrained by a maximum root depth.


<div class="fig-input">
```{r root-front-velocity-temp, fig.asp = 1, fig.cap='Root depth'}
path <- 'Wheat.Root.RootFrontVelocity.TemperatureFactor'
plot_xypair(pmf, path, x_lab = 'Environmental stress', y_lab = 'Multiplier of branching rate',
           label = c('Nitrogen stress', 'Total coverage', 'Water stress'))

```
</div>



<div class="fig-input">
```{r root-front-velocity, fig.asp = 1, fig.cap='Root depth'}
y_cols <- c('Wheat.Root.RootFrontVelocity')
plot_report(report, x_var, y_cols, x_lab = x_lab, 
            y_lab = 'Root depth (mm)')

```
</div>



<div class="fig-output">
```{r root-depth, fig.asp = 1, fig.cap='Root depth'}
y_cols <- c('Wheat.Root.Depth')
plot_report(report, x_var, y_cols, x_lab = x_lab, 
            y_lab = 'Root depth (mm)')

```
</div>



Root length growth is calculated using the daily DM partitioned to roots and a specific root length.  Root proliferation in layers is calculated using an approach similar to the generalised equimarginal criterion used in economics.  The uptake of water and N per unit root length is used to partition new root material into layers of higher 'return on investment'.


<div class="fig-output">
```{r root-length, fig.asp = 1, fig.cap='Root length'}
y_cols <- c('Wheat.Root.Length')
plot_report(report, x_var, y_cols, x_lab = x_lab, 
            y_lab = 'Root length (m?)')

```
</div>





## Supply {#sec:root-supply}

No biomass supply is considered in the `Root` organ (Fig. \@ref(fig:root-supply)).

<div class="fig-output">
```{r root-supply, fig.asp = 0.5, fig.cap='Biomass supply from root'}
y_cols <- c('Wheat.Root.DMSupply.Fixation',
            'Wheat.Root.DMSupply.Retranslocation',
            'Wheat.Root.DMSupply.Reallocation')

plot_report(report, x_var2, y_cols, x_lab = x_lab, 
            y_lab = 'Demand (g/d)', ncol = 3)

```
</div>


## Demand {#sec:root-demand}

The daily biomass demand of `Root` is calculated as a fraction of daily fixation (i.e. photosynthesis) from Stage 3 (`Emergence`) to Stage 8 (`End of grain filling`). The fraction of root demand is 0.2 until `Flowering time`, then reduces into 0.02 until `End of grain filling` (Fig. \@ref(fig:root-demand-fraction)). Only structural demand is considered in the `Root` organ (Fig. \@ref(fig:root-demand)). 



```{block, type='rmdnote', echo=TRUE}
Photosynthate is not partitioned into root after heading [@Fangsituassessmentnew2016].
```



<div class="fig-input">
```{r root-demand-fraction, fig.asp = 0.5, fig.cap='Fraction of root demand in the total fixation '}
y_cols <- c('Wheat.Root.DMDemandFraction')
plot_report(report, x_var2, y_cols, x_lab = x_lab, 
            y_lab = 'Fraction of total fixation', ncol = 3)

```
</div>




<div class="fig-output">
```{r root-demand, fig.asp = 1, fig.cap='Biomass demand by root'}
y_cols <- c('Wheat.Root.DMDemand.Structural',
'Wheat.Root.DMDemand.Storage',
'Wheat.Root.DMDemand.Metabolic')


plot_report(report, x_var, y_cols, x_lab = x_lab, 
            y_lab = 'Demand (g/d)', ncol = 3)

```
</div>

## Biomass dynamic {#sec:root-biomass}

The actual allocation (Fig. \@ref(fig:root-allocated)) is determined by the actual daily biomass supply (Fig. \@ref(fig:biomass-supply-total)) which may be smaller than than biomass demand (Fig. \@ref(fig:root-demand)). 

<div class="fig-output">
```{r root-allocated, fig.asp = 1, fig.cap='Actual allocated biomass for root'}
y_cols <- c('Wheat.Root.Allocated.StructuralWt',
'Wheat.Root.Allocated.StorageWt',
'Wheat.Root.Allocated.MetabolicWt')


plot_report(report, x_var, y_cols, x_lab = x_lab, 
            y_lab = 'Biomass (g/m2)', ncol = 3)

```
</div>

The daily loss of roots is calculated using a SenescenceRate function (0.005 in the default value).  All senesced material is automatically detached and added to the soil fresh organic matter (FOM) pool.  

<div class="fig-output">
```{r root-detached, fig.asp = 1, fig.cap='Detached biomass from root into soil organic.'}
y_cols <- c('Wheat.Root.Detached.StructuralWt',
'Wheat.Root.Detached.StorageWt',
'Wheat.Root.Detached.MetabolicWt')
plot_report(report, x_var, y_cols, x_lab = x_lab, 
            y_lab = 'Biomass (g/m2)', ncol = 3)

```
</div>


Finally `Root` biomass increases until `flowering time`, then gradually decreases as the senescence is more than allocation (Fig. \@ref(fig:root-weight)). All biomass is allocated into `Live` component (Fig. \@ref(fig:root-live)), as the senescenced `Root` immediately is detached and contributed into soil FOM (Fig. \@ref(fig:root-dead)).

<div class="fig-output">
```{r root-weight, fig.asp = 1, fig.cap='Dynamic of root biomass (Total)'}
y_cols <- c('Wheat.RootWt')
plot_report(report, x_var, y_cols, x_lab = x_lab, 
            y_lab = 'Biomass (g/m2)', ncol = 3)

```
</div>



<div class="fig-output">
```{r root-live, fig.asp = 1, fig.cap='Dynamic of root biomass (Live component)'}
y_cols <- c('Wheat.Root.Live.StructuralWt',
'Wheat.Root.Live.StorageWt',
'Wheat.Root.Live.MetabolicWt')
plot_report(report, x_var, y_cols, x_lab = x_lab, 
            y_lab = 'Biomass (g/m2)', ncol = 3)

```
</div>


<div class="fig-output">
```{r root-dead, fig.asp = 0.5, fig.cap='Dynamic of root biomass (Dead component)'}
y_cols <- c('Wheat.Root.Dead.StructuralWt',
'Wheat.Root.Dead.StorageWt',
'Wheat.Root.Dead.MetabolicWt')
plot_report(report, x_var2, y_cols, x_lab = x_lab, 
            y_lab = 'Biomass (g/m2)', ncol = 3)

```
</div>


