# Root {#cha:root}


```{r setup, message=FALSE, warning=FALSE, echo=FALSE}
source('_setup.R')
```


Only `Structural` is considered in the three components of biomass for `Root`. The biomass allocation depending on the fraction of daily fixation (i.e. photosynthesis).



## Root length {#sec:root-length}


<div class="fig-output">
```{r root-length, fig.asp = 1, fig.cap='Root length'}
y_cols <- c('Wheat.Root.Length')
plot_report(report, x_var, y_cols, x_lab = x_lab, 
            y_lab = 'Root length (m?)')

```
</div>





## Supply {#sec:root-supply}

No biomass supply is considered in the `Root` organ (Fig. \@ref(fig:root-supply)).

<div class="fig-output">
```{r root-supply, fig.asp = 0.5, fig.cap='Biomass supply from root'}
y_cols <- c('Wheat.Root.DMSupply.Fixation',
            'Wheat.Root.DMSupply.Retranslocation',
            'Wheat.Root.DMSupply.Reallocation')

plot_report(report, x_var2, y_cols, x_lab = x_lab, 
            y_lab = 'Demand (g/d)', ncol = 3)

```
</div>


## Demand {#sec:root-demand}

The daily biomass demand of `Root` is calculated as a fraction of daily fixation (i.e. photosynthesis) from Stage 3 (`Emergence`) to Stage 8 (`End of grain filling`). The fraction of root demand is 0.2 until `Flowering time`, then reduces into 0.02 until `End of grain filling` (Fig. \@ref(fig:root-demand-fraction)). Only structural demand is considered in the `Root` organ (Fig. \@ref(fig:root-demand)). 



```{block, type='rmdnote', echo=TRUE}
Photosynthate is not partitioned into root after heading [@Fangsituassessmentnew2016].
```



<div class="fig-input">
```{r root-demand-fraction, fig.asp = 0.5, fig.cap='Fraction of root demand in the total fixation '}
y_cols <- c('Wheat.Root.DMDemandFraction')
plot_report(report, x_var2, y_cols, x_lab = x_lab, 
            y_lab = 'Fraction of total fixation', ncol = 3)

```
</div>




<div class="fig-output">
```{r root-demand, fig.asp = 1, fig.cap='Biomass demand by root'}
y_cols <- c('Wheat.Root.DMDemand.Structural',
'Wheat.Root.DMDemand.Storage',
'Wheat.Root.DMDemand.Metabolic')


plot_report(report, x_var, y_cols, x_lab = x_lab, 
            y_lab = 'Demand (g/d)', ncol = 3)

```
</div>

## Biomass dynamic {#sec:root-biomass}

The actual allocation (Fig. \@ref(fig:root-allocated)) is determined by the actual daily biomass supply (Fig. \@ref(fig:biomass-supply-total)) which may be smaller than than biomass demand (Fig. \@ref(fig:root-demand)). 

<div class="fig-output">
```{r root-allocated, fig.asp = 1, fig.cap='Actual allocated biomass for root'}
y_cols <- c('Wheat.Root.Allocated.StructuralWt',
'Wheat.Root.Allocated.StorageWt',
'Wheat.Root.Allocated.MetabolicWt')


plot_report(report, x_var, y_cols, x_lab = x_lab, 
            y_lab = 'Biomass (g/m2)', ncol = 3)

```
</div>

The daily loss of roots is calculated using a SenescenceRate function (0.005 in the default value).  All senesced material is automatically detached and added to the soil fresh organic matter (FOM) pool.  

<div class="fig-output">
```{r root-detached, fig.asp = 1, fig.cap='Detached biomass from root into soil organic.'}
y_cols <- c('Wheat.Root.Detached.StructuralWt',
'Wheat.Root.Detached.StorageWt',
'Wheat.Root.Detached.MetabolicWt')
plot_report(report, x_var, y_cols, x_lab = x_lab, 
            y_lab = 'Biomass (g/m2)', ncol = 3)

```
</div>


Finally `Root` biomass increases until `flowering time`, then gradually decreases as the senescence is more than allocation (Fig. \@ref(fig:root-weight)). All biomass is allocated into `Live` component (Fig. \@ref(fig:root-live)), as the senescenced `Root` immediately is detached and contributed into soil FOM (Fig. \@ref(fig:root-dead)).

<div class="fig-output">
```{r root-weight, fig.asp = 1, fig.cap='Dynamic of root biomass (Total)'}
y_cols <- c('Wheat.RootWt')
plot_report(report, x_var, y_cols, x_lab = x_lab, 
            y_lab = 'Biomass (g/m2)', ncol = 3)

```
</div>



<div class="fig-output">
```{r root-live, fig.asp = 1, fig.cap='Dynamic of root biomass (Live component)'}
y_cols <- c('Wheat.Root.Live.StructuralWt',
'Wheat.Root.Live.StorageWt',
'Wheat.Root.Live.MetabolicWt')
plot_report(report, x_var, y_cols, x_lab = x_lab, 
            y_lab = 'Biomass (g/m2)', ncol = 3)

```
</div>


<div class="fig-output">
```{r root-dead, fig.asp = 0.5, fig.cap='Dynamic of root biomass (Dead component)'}
y_cols <- c('Wheat.Root.Dead.StructuralWt',
'Wheat.Root.Dead.StorageWt',
'Wheat.Root.Dead.MetabolicWt')
plot_report(report, x_var2, y_cols, x_lab = x_lab, 
            y_lab = 'Biomass (g/m2)', ncol = 3)

```
</div>


