# Spike {#cha:spike}


```{r spike-setup, message=FALSE, warning=FALSE, echo=FALSE}
source('_setup.R')
```

`Spike` provides biomass through retranslocation, requires biomass depending on the population and potential spike weight. The biomass is allocated into two components, i..e `Structural` and `Storage`. No `Metabolic` is considered.

## Supply {#sec:spike-supply}

In `Spike`, the biomass supply only sources from retranslocation (Fig. \@ref(fig:spike-supply)). Daily retranslocation is the proportion of current storage ($W_{spike, storage}$). The default value of proportion is 0.5 since `StartGrainFill`, i.e. retranslocatable biomsss is 50% during grain filling (Fig. \@ref(fig:spike-retran-factor)).



<div class="fig-input">
```{r spike-retran-factor, fig.asp = 0.5, fig.cap='Growth duration of spike development'}
y_cols <- c('Wheat.Spike.DMRetranslocationFactor')
g_report %>% 
    # filter(Wheat.Phenology.Stage > 5) %>% 
    plot_report(g_xvar2, y_cols, x_lab = g_xlab,
            y_lab = 'Factor of retranslocation ([-])')
```
</div>


 

<div class="fig-output">
```{r spike-supply, fig.asp = 1, fig.cap='Biomass supply from spike'}
y_cols <- c('Wheat.Spike.DMSupply.Fixation',
            'Wheat.Spike.DMSupply.Retranslocation',
            'Wheat.Spike.DMSupply.Reallocation')

plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Biomass supply (g biomamss '~m^-2~" ground "~d^-1~')'),
            ncol = 3)

```
</div>


## Demand {#spike-demand}

The Structural demand of `Spike` ($D_{spike, structural}$) is determined by the population based demand function since Stage 5 (`FlagLeaf`) to Stage 7 (`StartGrainFill`). The structural demand includes the growth respiration. 

$$
D_{spike, structural} = \Delta TT \times N_{head} \frac {W_{max, grain}}{T_{growth}} \times F_{spike, structure} / C_{spike, efficiency}
$$
where $\Delta TT$ is the daily thermal time in the phenology module (Fig. \@ref(fig:phenology-tt)); $N_{head}$ is the head number per unit area, i.e. total stem population at flowering time (Fig. \@ref(fig:str-live-stem-number)); $W_{max, grain}$ is the potential weight per spike (g) with default value `r get_fixed_value(g_pmf, 'Wheat.Spike.DMDemandFunction.MaximumOrganWt')`; $T_{growth}$ is the growth duration of spike ($TT$, the thermal time target from `FlagLeaf` to `StartGrainFill`). As the target of `EarlyReproductive` is sensitive to photoperiod (Section \@ref(sec:phe-stage-period)), the growth duration can be changed during spike development depending on the photoperiod (Fig. \@ref(fig:spike-growth-duration)). The head number, growth duration and potential spike weight are defined as potential spike weight including the structural and storage conponents and the growth respiration. 


$F_{spike, structure}$ is the structura fraction of `Spike` with default value `e get_fixed_value(g_pmf, 'Wheat.Spike.StructuralFraction')`. $C_{spike,efficiency}$ is the conversion efficiency of `Spike`, i.e. the efficiency of alloction biomass converted into carbon (growth respiration). $C_{efficiency}$ has the default value `r get_fixed_value(g_pmf, 'Wheat.Spike.DMConversionEfficiency')` and is counted befor allocation. 


<div class="fig-output">
```{r spike-number, fig.asp = 1, fig.cap='Head number'}
y_cols <- c('Wheat.Spike.HeadNumber',
            'Wheat.Leaf.LiveStemNumber',
            'Wheat.Structure.TotalStemPopn')
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Demand (g biomass'~m^-2~' ground ' ~d^-1~')'),
            ncol = 3)
```
</div>


<div class="fig-input">
```{r spike-growth-duration, fig.asp = 0.5, fig.cap='Growth duration of spike development'}

y_cols <- c('Wheat.Spike.DMDemandFraction.GrowthDuration')
g_report %>% 
    filter(Wheat.Phenology.Stage > 5) %>% 
    plot_report(g_xvar2, y_cols, x_lab = g_xlab2,
            y_lab = expression('Growth duration ('*degree*'Cd)'))
```
</div>



Storage demand is to fill the non-structural components (i.e. storage for `Spike`). Current structural biomass and structural demand are used to calculate the potential total biomass of `Spike` (structural plus storage). The difference of potental total biomas and current biomass are the storage demand. Storage demand also include the growth respiration.    

$$
D_{spike, storage} = \frac {(W_{spike, structural} + D_{spike, structural}) / F_{spike, structure} - W_{spike, structural} + W_{spike, storage} + D_{spike, structural}} {C_{spike, efficiency}}
$$

No metabolic demand is calculated for `Spike`. 


The figure below shows the demands of `Spike` in the test simulation (Fig. \@(fig:spike-demand)).

<div class="fig-output">
```{r spike-demand, fig.asp = 1, fig.cap='Biomass demand by spike'}
y_cols <- c('Wheat.Spike.DMDemand.Structural',
            'Wheat.Spike.DMDemand.Metabolic',
            'Wheat.Spike.DMDemand.Storage')
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Demand (g biomass'~m^-2~' ground ' ~d^-1~')'),
            ncol = 3)
```
</div>


## Biomass dynamic {#spike-biomass}

The actual allocation reflects the increase of structural component, and retranslocation of storage component (Fig. \@ref(fig:spike-allocated)). `Spike` only considers the `Live` biomass (Fig. \@ref(fig:spike-live), no `Dead` biomass (Fig. \@ref(fig:spike-dead)).


<div class="fig-output">
```{r spike-allocated, fig.asp = 1, fig.cap='Actual allocated biomass for spike'}
y_cols <- c('Wheat.Spike.Allocated.StructuralWt',
            'Wheat.Spike.Allocated.MetabolicWt',
            'Wheat.Spike.Allocated.StorageWt')
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Allocated biomass (g biomass '~m^-2~" ground "~d^-1~')'), 
            ncol = 3)

```
</div>



<div class="fig-output">
```{r spike-weight, fig.asp = 1, fig.cap='Dynamic of spike biomass (Total)'}
y_cols <- c('Wheat.SpikeWt')
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Biomass (g biomass '~m^-2~' ground)'))

```
</div>



<div class="fig-output">
```{r spike-live, fig.asp = 1, fig.cap='Dynamic of spike biomass (Live component)'}
y_cols <- c('Wheat.Spike.Live.StructuralWt',
            'Wheat.Spike.Live.MetabolicWt',
            'Wheat.Spike.Live.StorageWt')
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Biomass (g biomass '~m^-2~' ground)'),
            ncol = 3)

```
</div>


<div class="fig-output">
```{r spike-dead, fig.asp = 0.5, fig.cap='Dynamic of spike biomass (Dead component)'}
y_cols <- c('Wheat.Spike.Dead.StructuralWt',
            'Wheat.Spike.Dead.MetabolicWt',
            'Wheat.Spike.Dead.StorageWt')


plot_report(g_report, g_xvar2, y_cols, x_lab = g_xlab2, 
            y_lab = expression('Biomass (g biomass '~m^-2~' ground)'), 
            ncol = 3)

```
</div>
