# Stem {#cha:stem}

```{r stem-setup, message=FALSE, warning=FALSE, echo=FALSE}
source('_setup.R')
```


`Stem` provides biomass through retranslocation, requires biomass a proportion of daily fixation (i.e. photosynthesis in `Leaf`). The biomass is allocated into two components, i..e `Structural` and `Storage`. No `Metabolic` is considered.


## Supply {#sec:stem-supply}

In `Stem`, the biomass supply only sources from retranslocation (Fig. \@ref(fig:stem-supply)). Daily retranslocation is the proportion of current storage ($W_{stem, storage}$). The default value of proportion is 0.5 since `StartGrainFill`, i.e. retranslocatable biomsss is 50% during grain filling (Fig. \@ref(fig:stem-retran-factor)).


<div class="fig-input">
```{r stem-retran-factor, fig.asp = 0.5, fig.cap='Growth duration of stem development'}
y_cols <- c('Wheat.Stem.DMRetranslocationFactor')
report %>% 
    # filter(Wheat.Phenology.Stage > 5) %>% 
    plot_report(x_var2, y_cols, x_lab = x_lab,
            y_lab = 'Growth duration (oCd)')
```
</div>



<div class="fig-output">
```{r stem-supply, fig.asp = 1, fig.cap='Biomass supply from stem'}
y_cols <- c('Wheat.Stem.DMSupply.Fixation',
            'Wheat.Stem.DMSupply.Retranslocation',
            'Wheat.Stem.DMSupply.Reallocation')

plot_report(report, x_var, y_cols, x_lab = x_lab, 
            y_lab = 'Demand (g/d)', ncol = 3)

```
</div>


## Demand {#sec:stem-demand}

The daily biomass demand of `Stem` is calculated as a fraction of daily fixation (i.e. photosynthesis) from Stage 3 (`Emergence`) to Stage 6 (`Flowering time`) (Fig. \@ref(fig:stem-demand-fraction)) and increases at Stage 4 (`Terminal spikelet`) (Fig. \@ref(fig:stem-demand-fraction)). After `Flowering time`, no biomass allocated into stem (Fig. \@ref(fig:stem-demand)).  

<div class="fig-input">
```{r stem-demand-fraction, fig.asp = 1, fig.cap='Fraction of stem demand in the total fixation '}
y_cols <- c('Wheat.Stem.DMDemandFraction')
plot_report(report, x_var, y_cols, x_lab = x_lab, 
            y_lab = 'Fraction of total fixation')

```
</div>




<div class="fig-output">
```{r stem-demand, fig.asp = 1, fig.cap='Biomass demand by stem'}
y_cols <- c('Wheat.Stem.DMDemand.Structural',
'Wheat.Stem.DMDemand.Storage',
'Wheat.Stem.DMDemand.Metabolic')


plot_report(report, x_var, y_cols, x_lab = x_lab, 
            y_lab = 'Demand (g/d)', ncol = 3)

```
</div>

## Biomass dynamic {#sec:stem-biomass}

The actual allocation reflects the increase of structural component, and retranslocation of storage component (Fig. \@ref(fig:stem-allocated)). `Stem` only considers the `Live` biomass (Fig. \@ref(fig:stem-live), no `Dead` biomass (Fig. \@ref(fig:stem-dead)).


<div class="fig-output">
```{r stem-allocated, fig.asp = 1, fig.cap='Actual allocated biomass for stem'}
y_cols <- c('Wheat.Stem.Allocated.StructuralWt',
'Wheat.Stem.Allocated.StorageWt',
'Wheat.Stem.Allocated.MetabolicWt')


plot_report(report, x_var, y_cols, x_lab = x_lab, 
            y_lab = 'Biomass (g/m2)', ncol = 3)

```
</div>


<div class="fig-output">
```{r stem-weight, fig.asp = 1, fig.cap='Dynamic of stem biomass (Total)'}
y_cols <- c('Wheat.StemWt')
plot_report(report, x_var, y_cols, x_lab = x_lab, 
            y_lab = 'Biomass (g/m2)')

```
</div>




<div class="fig-output">
```{r stem-live, fig.asp = 1, fig.cap='Dynamic of stem biomass (Live component)'}
y_cols <- c('Wheat.Stem.Live.StructuralWt',
'Wheat.Stem.Live.StorageWt',
'Wheat.Stem.Live.MetabolicWt')


plot_report(report, x_var, y_cols, x_lab = x_lab, 
            y_lab = 'Biomass (g/m2)', ncol = 3)

```
</div>


<div class="fig-output">
```{r stem-dead, fig.asp = 0.5, fig.cap='Dynamic of stem biomass (Dead component)'}
y_cols <- c('Wheat.Stem.Dead.StructuralWt',
'Wheat.Stem.Dead.StorageWt',
'Wheat.Stem.Dead.MetabolicWt')


plot_report(report, x_var2, y_cols, x_lab = x_lab, 
            y_lab = 'Biomass (g/m2)', ncol = 3)

```
</div>




