# Structure {#cha-structure}



```{r str-setup, message=FALSE, warning=FALSE, echo=FALSE}
source('_setup.R')
```

The development of wheat leaves and tillers are simulated with an apex model which is further developed from leaf cohort model [@BrownPlantModellingFramework2014]. The basic assumptions include

1. The growth and development of a plant is controlled by apex. Only one apex is existed in a plant at emergence. Branching increases the total apex number of a plant. Apex death decreases the apex number, which are caused by several reasons including the carbon allocation, light intensity, natural death. The apex number is not necessary as an integer to simulate plant development in the population level. 
2.	The number of apex in a plant determines the number of the new leaves when initialization of a new cohort. The cohort size is fixed after initialization although attributes can be changed in the later stage. 
3.	The apexes are grouped by age and have the same age if they initialize at the same day. During development of new cohort, new apexes caused by branching develops into new tillers which have the same behaviours during the whole lift span (e.g. size, area, nitrogen, photosynthesis). The apex age equals to 1 when it initialize and increases by 1 when a new leaf cohort initializes. Each apex group has several attributes including size and age.  
4.	The leaves in a cohort also are distinguished and grouped by apex ages, which determines at the initialization of leaf cohort. 
5.	Death of branches or tillers only reduces the total number of apexes, not the size of existing cohorts. The apexes with youngest age are going to death first. 



## Phyllochron {#sec:str-phyllochron}

The phyllochron is the intervening period between the sequential emergence of leaf tips on the main stem of a wheat [@mcmaster_re-examining_2003].

The non-linear reponse of temperature on phyllchron were observed by Friend et al. [-@friend_leaf_1962] and Cao and Moss [-@cao_temperature_1989]. The soil temperature provided more accurately prediction of leaf development than air temperature [@JamiesonPredictionleafappearance1995]. However, a simple linear reponse of phyllochron to air temperature works surprusingly well in predicting phyllochron for most field conditions [@mcmaster_re-examining_2003]. If improvements are desired, the use of non-linear reponses and soil temperature shows promise [@JamiesonPredictionleafappearance1995; @YanEquationModellingTemperature1999]. Consequently, we assume the linear reponse of air temperature on leaf appearance (phyllochorn).  


The base phyllochron is a genotypic parameter with default value `r get_fixed_value(g_pmf, 'Wheat.Structure.Phyllochron.BasePhyllochron')`, but is chagned for most of cultivars. Based on [@JamiesonPredictionleafappearance1995], leaf appearance could be described by a base phyllochron determined between leaves 3 and 7 and a phyllochron that was 70% of base phyllochron for leaves < 3 and 140% of base phyllochroen for leaves > 7 (Fig. \@ref(fig:str-phyllochron-age)). The phyllochron also is adjusted by photoperiod [reference required] through increasing pholochron in the shorter day length (Fig. \@ref(fig:str-phyllochron-ppd)).


<div class="fig-input">
```{r str-phyllochron-age, fig.asp = 0.5, fig.cap='Phyllochron of leaf cohort is depending on the rank on the main stem'}
path <- 'Wheat.Structure.Phyllochron.LeafStageFactor'
plot_xypair(g_pmf, path, x_lab = 'Appeared cohorted number', y_lab = 'Mulitiplier of base phyllochron') +
    scale_x_continuous(breaks = seq(1, 14))

```
</div>



<div class="fig-input">
```{r str-phyllochron-ppd, fig.asp = 0.5, fig.cap='The multiplier of phyllochron which is effected by daily photoperiod length.'}
path <- 'Wheat.Structure.Phyllochron.PhotoPeriodEffect'
plot_xypair(g_pmf, path, x_lab = 'Daily photoperiod (h)', y_lab = 'Mulitiplier of base phyllochron') +
    scale_x_continuous(breaks = seq(6, 15))

```
</div>

Finally, the phyllochron is dynamically adjusted according to appeared cohort number and daily photoperiod (Fig. \@ref(fig:str-phyllochron)). 

<div class="fig-output">
```{r str-phyllochron, fig.asp=1, fig.cap='The actual phyllochron in the testing environment'}
y_cols <- c(
    'Wheat.Structure.Phyllochron')
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, y_lab = 'Phyllochron (oCd)')

```
</div>


## Final leaf number {#sec:final-leaf-number}


Will be documented...

<div class="fig-output">
```{r str-final-leaf-number, fig.asp=0.5, fig.cap='Final leaf number in main stem'}
y_cols <- c(
    'Wheat.Structure.FinalLeafNumber')
plot_report(g_report, g_xvar2, y_cols, x_lab = g_xlab, y_lab = 'Final node number in main stem')

```
</div>

## Initialization and appearance of leaf tips on main stem {#sec:main-stem}

At `Germination` stage, `r node_count(g_pmf, '//LeafCohort')` new leaf cohorts or tips are initialized at the main stem. At `Emergence` stage, `r sum(get_xml_value(g_pmf, '//LeafCohort//Area') > 0)` leaf cohort or tip is appeared at the main stem, and `r sum(get_xml_value(g_pmf, '//LeafCohort//Area') > 0)` more leaf cohort is initialized. The potential appearance of leaf tip number ($N_{p, tip}$) is initialized as `r sum(get_xml_value(g_pmf, '//LeafCohort//Area') > 0)`. 

After `Emergence`, the potential appearance of tip number in the main stem ($N_{p, tip}$) is daily increased according to the daily phyllochron (Fig. \@ref(fig:str-phyllochron)) and thermal time (Section \@ref(sec:phe-thermal-time)) until `Maturity` (Fig. \@ref(fig:str-delta-tip) and \@ref(fig:str-tips). $N_{p, tip}$ should stop increasing when final leaf number is reached). 



$$
 \Delta N_{p, tip} = \frac{\Delta TT_{t}}{P_{phy}}
$$

where, $N_{p, tip}$ is the daily increase of leaf tip number (Fig. \@ref(fig:str-delta-tip)), $\Delta TT_{t}$ is the daily thermal time, $P_{phy}$ is the phyllochron calculated at today. 


<div class="fig-output">
```{r str-delta-tip, fig.asp=0.5, fig.cap='Daily increase of tip number in main stem. There is no point to consider increase of tip number after stage 4 (terminal spikelet), although model exports increase of tip number in the whole growth season'}
y_cols <- c('Wheat.Structure.DeltaTipNumber')
g_report %>% 
    # filter(Wheat.Phenology.Stage <= 4) %>% 
    plot_report(g_xvar2, y_cols, x_lab = g_xlab, 
            y_lab = 'Daily increase of tip number')
```
</div>


Potential appearance of tip number in main stem ($N_{p, tip}$) are summarized daily increases since `Emergence`, plus the appeared leaf tip at `Emergence` (`r sum(get_xml_value(g_pmf, '//LeafCohort//Area') > 0)` for wheat model) (Fig. \@ref(fig:str-tips)).


$$
    N_{p, tip}=\sum_{t=T_{0}}^{T}\Delta N_{p, tip} + 1
$$

where, $T_{0}$ is day of `Emergence`.  $T$ is today. In the Structure model, the tip numbers are not calculated for branches or tillers, but only for main stem (Figure \@ref(fig:str-tips)). 

Before plant reaches the final leaf number (i.e. all leaves are initialized and appeared), a new leaf cohort is initialized and appeared when increases of $N_{p, tip}$ are more than 1 (Figure \@ref(fig:str-delta-tip)). Consequently, the rates of leaf initialization and appearance are same, except initialized tip number is more than `r node_count(g_pmf, '//LeafCohort')`  of appeared tip number.

<div class="fig-output">
```{r str-tips, fig.asp=1, fig.cap='Tips number in main stem. The potential appeared tip number keeps increasing after flag leaf, which is only a model output and need to be fixed.'}
y_cols <- c('Wheat.Structure.CohortToInitialise',
    'Wheat.Structure.PotLeafTipsAppeared', 
    'Wheat.Structure.LeafTipsAppeared')
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = 'Number', ncol = 3)
```
</div>


Huan stage is exported as the output variable `LeafTipsAppeared`.    

<div class="fig-output">
```{r str-haun-stage, fig.cap='Haun stage in main stem'}
y_cols <- c('Wheat.Structure.HaunStage')
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = 'Haun stage', ncol = 3)

```
</div>



The fraction of final leaf is used to simulate the variation of final leaf number in a population. The fraction of leaf cohort is set as 1 for all leaf cohort, except the flag leaf which equal to decimal part of final leaf number (Fig. \@ref(fig:str-final-leaf-number)). 

<div class="fig-output">
```{r str-leaf-fraction, fig.asp=0.5, fig.cap='Fraction of leaf cohort'}
y_cols <- c(
    'Wheat.Structure.NextLeafProportion')
plot_report_rank(g_report, y_cols, y_lab = 'Fraction of leaf cohort')
```
</div>









## Tillering {#sec:str-tillering}

At `Emergence`, the apex number equals to `1`. The apex number in a plant ($A$) is increased by branching ($\Delta A_{B} $) and decreased by mortality ($\Delta A_{M} $) in every day.
$$
A = \sum_{i=1}^{N_{node}}{(\Delta A_{B} - \Delta A_{M})}
$$



<div class="fig-output">
```{r str-apex-number, fig.asp=1, fig.cap='Apex number in the main stem'}
y_cols <- c('Wheat.Structure.ApexNum')
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = 'Number', ncol = 3)
```
</div>




### Branching rate

The branching rate in a plant is specified by parameter BranchingRate ($\Delta A_{B}$) and is calculated as potential branching rate (Fig. \@ref(fig:str-branching-rate)) and several stress factors (i.e. nitrogen stress, total coverage, and water stress). From stage Emergence to Terminal Spikelet (Section \@ref(sec:phe-stage-period)), the potential branching rate is defined as a function of number of appeared cohorts in the main stem (Figure \@ref(fig:str-branching-rate)) which follow the pattern of Fibonacci sequence. Beyond this period, the branching rate is set as zero. 

<div class="fig-input">
```{r str-branching-rate, fig.asp = 0.5, fig.cap='Potential branching rate of APSIM-Wheat as a function of appreared cohort number'}
path <- 'Wheat.Structure.BranchingRate.PotentialBranchingRate.Vegetative.PotentialBranchingRate'
plot_xypair(g_pmf, path, x_lab = 'Number of appeared cohorts', y_lab = 'Branching rate')

```
</div>



Two stresses are defined in the APSIM-Wheat including nitrogen and WSC. A simple sensitivity analysis indicates the branching rate is too sensitive to WSC with default values (x = [0.1, 0.2]; y = [0, 1]). So, this feature is disabled for further analysis. 

The nitrogen stress is calculated as a function of fraction of nitrogen supply relative to nitrogen demand which is exported from the Arbitrator module. Wheat module assumes no nitrogen stress when the nitrogen supply is bigger than 1.5 times of nitrogen demand (Figure \@ref(fig:str-branching-factor)). Nitrogen stress linearly increases when supply/demand ratio less then 1.5 (<font color="red">Reference required.</font>)


<div class="fig-input">
```{r str-branching-factor, fig.asp = 1.25, fig.cap='The factors to influence of branching rate (nitrogen stress, total coverage and water stress). The final multiplier of branching rate is the minimum values of the '}
path <- paste0('Wheat.Structure.BranchingRate.StressFactors.',
                c('NitrogenEffect', 'CoverEffect', 'WaterStressEffect'))
plot_xypair(g_pmf, path, x_lab = 'Environmental stress', y_lab = 'Multiplier of branching rate',
           label = c('Nitrogen stress', 'Total coverage', 'Water stress'))

```
</div>



<div class="fig-output">
```{r str-branching-stress, fig.cap='The stress factors for branching rate'}
y_cols <- c('Wheat.Structure.BranchingRate.StressFactors.NitrogenEffect', 
            'Wheat.Structure.BranchingRate.StressFactors.CoverEffect',
            'Wheat.Structure.BranchingRate.StressFactors.WaterStressEffect')
y_labels <- c('Nitrogen', 'Cover', 'Water')
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = 'Stress factor', ncol = 3, y_labels = y_labels)

```
</div>






Figure \@ref(fig:str-tiller-number) shows the branching rate and total branching number in the test simulation without nitrogen stress on branching rate during branching period (from Emergence to Terminal Spikelet.

<div class="fig-output">
```{r str-tiller-number, fig.cap='The branching rate and branch number for wheat'}
y_cols <- c('Wheat.Structure.BranchNumber', 
            'Wheat.Structure.BranchingRate',
            'Wheat.Structure.BranchMortality')

plot_report(g_report, g_xvar, y_cols, ncol = 3,
            x_lab = g_xlab, y_lab = 'Branch number or branching rate') 

```
</div>





### Mortality {#sec-structure-mortality}

Two types of mortality are considered in the apex model, i.e. smaller tiller at terminal spikelet and low growth rate. For any types of tiller mortality, the plant does not reduce the population of existing leaf cohort, but number of apex, then reduce the population size of new leaf cohort. 

At the terminal spikelet, all tillers with less than `r get_fixed_value(g_pmf, 'Wheat.Structure.StemSenescenceAge')` leaves are stopped to growth new leaves.



Branching mortality starts from the Flag leaf until Flowering which defines as a function of moving mean tiller growth rate (Figure \@ref(fig:str-mortality-growth-rate). The mean tiller growth rate is calculated as the 5 days moving means of tiller growth rate, which is calculated by the daily biomass supply divides thermal time and total stem population.  <font color="red">Reference required.</font>


<div class="fig-input">
```{r str-mortality-growth-rate, fig.asp=0.75, fig.cap='Tiller mortality as a function of moving mean tiller growth rate'}
path <- 'Wheat.Structure.BranchMortality.MortalityPhase.Mortality.MortalityPerDegDay'
plot_xypair(g_pmf, path, x_lab = 'Moving mean tiller growth rate', y_lab = 'Branch motality')
```
</div>





Figure \@ref(fig:str-tiller-growth-rate) shows the mean tiller growth rate and the three factors to calculate it in the test simulation.

<div class="fig-output">
```{r str-tiller-growth-rate, fig.cap='The moving tiller growth rate'}
y_cols <- c(
    'Wheat.Structure.MeanTillerGrowthRate')
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, y_lab = 'Moving tiller growth rate')

```
</div>




<div class="fig-output">
```{r str-tiller-number-mo, fig.cap='The mortality of tillers'}
y_cols <- c(

    'Wheat.Structure.BranchMortality',
    'Wheat.Structure.ProportionBranchMortality',
            'Wheat.Structure.ProportionPlantMortality')
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, y_lab = 'Mortality of branching', ncol = 3)

```
</div>




## Plant and Main-Stem Population

No plant mortality is considerred in the wheat model. 

<div class="fig-output">
```{r str-population, fig.asp = 0.5, fig.cap='Plant population.'}
y_cols <- c('Wheat.Structure.MainStemPopn')
plot_report(g_report, g_xvar2, y_cols, x_lab = 'Growth stage', y_lab = 'Plant population', ncol = 3)

```
</div>




<div class="fig-output">
```{r str-live-stem-number, fig.cap='Total stem population and live stem number.'}
y_cols <- c('Wheat.Structure.TotalStemPopn',
    'Wheat.Leaf.LiveStemNumber')
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, y_lab = 'Stem population', ncol = 3)

```
</div>



## Canopy height {#sec:canopy-height}
The canopy height (Fig. \@ref(fig:str-height)) is calculated as the potential height (Fig. \@ref(fig:str-potential-height)) and adjusted by water stress (Fig. \@ref(fig:str-height-water-stress)). 




<div class="fig-input">
```{r str-potential-height, fig.asp=0.5, fig.cap='Potential canopy height'}
path <- 'Wheat.Structure.HeightModel.PotentialHeight'
plot_xypair(g_pmf, path, x_lab = 'Stage', y_lab = 'Potential canopy height (mm)')
```
</div>


<div class="fig-input">
```{r str-height-water-stress, fig.asp=0.5, fig.cap='The impact of water stress on canopy height'}
path <- 'Wheat.Structure.HeightModel.WaterStress'
plot_xypair(g_pmf, path, x_lab = 'water-supply-demand-ratio', y_lab = 'Multiplier of water stress on canopy height')
```
</div>



<div class="fig-output">
```{r str-height, fig.cap='The simulated canopy height'}
y_cols <- c('Wheat.Structure.Height')

plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, y_lab = 'Canopy height (mm)')

```
</div>
