## Nitrogen {#sec:leaf-nigrogen}


### Functional nitrogen

Ratio of leaf functional nitrogen ($f_{N,\,leaf}$) quantifys the nitrogen stress status of the plant and represents the concentration of metabolic N relative the maximum potentil metabolic N content of the leaf.


$$
f_{N,\,leaf}=C_{leaf} / (\frac{C_{critical,\,leaf}-C_{min,\,leaf} \times S_{leaf}}{1-S_{leaf}})
$$

where $C_{N}$ is the nitrogen concentration of `Leaf` parts; $R_{N,\,expan}$ is multiplier for nitrogen deficit effect on phenology which is specified by `N_fact_photo` in the wheat.xml and default value is 1.5.

double functionalNConc = (CohortParameters.CriticalNConc.Value() -
                                          CohortParameters.MinimumNConc.Value() * CohortParameters.StructuralFraction.Value()) *
                                         (1 / (1 - CohortParameters.StructuralFraction.Value()));
                


<div class="fig-input">
```{r leaf-nconc, fig.asp = 1, fig.cap='Minimum, critical and maximum nitrogen concentration in leaf.'}
y_cols <- c('Wheat.Leaf.MinimumNConc',
'Wheat.Leaf.CriticalNConc',
'Wheat.Leaf.MaximumNConc')
y_labels <- c('Minimum', 'Critical', 'Maximum')
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
        y_lab = expression('Nitrogen concentration (g N'~g^-1~' leaf)'), 
        ncol = 3,
        y_labels = y_labels)

```
</div>


<div class="fig-output">
```{r leaf-nitrogen-functional-n, fig.asp=0.5, fig.cap='Ratio of functional nitrogen'}
y_cols <- c('Wheat.Leaf.Fn')
plot_report(g_report, g_xvar2, y_cols, x_lab = g_xlab2, 
            y_lab = 'Ratio of functional nitrogen[-]')

```
</div>





### Nitrogen demand


<div class="fig-output">
```{r leaf-nitrogen-demand, fig.asp=1, fig.cap='Nitrogen demand of leaf.'}
y_cols <- c('Wheat.Leaf.NDemand.Total',
            'Wheat.Leaf.NDemand.Structural', 
            'Wheat.Leaf.NDemand.Metabolic', 
            'Wheat.Leaf.NDemand.Storage')
plot_report(g_report, g_xvar, 
            y_cols, x_lab = g_xlab, 
            y_lab = expression('Nitrogen demand (g N ' ~m^-2~'ground)'),
            ncol = 4)
```
</div>




### Actual allocation {#sec:leaf-nitrogen-allocated}



<div class="fig-output">
```{r leaf-nitrogen-allocated, fig.asp = 1, fig.cap='Actual allocated nitrogen to leaf for three components. The negative values of Storage indicate nitrogen is ratranslocated into other organs.'}
y_cols <- sprintf('Wheat.Leaf.Allocated.%sN', g_demand)
            
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Allocated biomass (g biomass '~m^-2~' ground '~d^-1~')'),
            y_labels = g_demand, ncol = 3)


```
</div>



### Nitrogen contents {#sec:leaf-nitrogen-contents}

<div class="fig-output">
```{r leaf-nitrogen-wt, fig.asp = 1, fig.cap='Dynamic of leaf nitrogen for three components.'}
y_cols <- sprintf('Wheat.Leaf.%sN', g_demand)

plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Nitrogen contents (g N '~m^-2~' ground '~d^-1~')'),
            y_labels = g_demand,
            ncol = 4)

```
</div>




<div class="fig-output">
```{r leaf-nitrogen-live, fig.asp = 1, fig.cap='Dynamic of leaf nitrogen in Live pool for three components.'}
y_cols <- sprintf('Wheat.Leaf.Live.%sN', g_demand)

plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Nitrogen contents (g N '~m^-2~' ground '~d^-1~')'),
             y_labels = g_demand,
            ncol = 4)

```
</div>



<div class="fig-output">
```{r leaf-nitrogen-dead, fig.asp = 0.5, fig.cap='Dynamic of leaf nitrogen in Dead pool for three components.'}
y_cols <- sprintf('Wheat.Leaf.Dead.%sN', g_demand)

plot_report(g_report, g_xvar2, y_cols, x_lab = g_xlab2, 
            y_lab = expression('Nitrogen contents (g N '~m^-2~' ground '~d^-1~')'),
            y_labels = g_demand,
            ncol = 4)

```
</div>




### Nitrogen concentration {#sec:leaf-nitrogen-conc}

<div class="fig-output">
```{r leaf-nitrogen-concentration, fig.asp = 0.5, fig.cap='Dynamic of leaf nitrogen concentration in Live and Dead.'}
y_cols <- c('Wheat.Leaf.Live.NConc', 'Wheat.Leaf.Dead.NConc',
            "Wheat.Leaf.Nconc")

plot_report(g_report, g_xvar2, y_cols, x_lab = g_xlab2, 
            y_lab = expression(atop('Nitrogen concentration',
                                    '(g N '~g^-1~' biomass )')),
            y_labels = c("Live", "Dead", 'Whole leaf'),
            ncol = 4)
```
</div>




<div class="fig-output">
```{r leaf-nitrogen-concentration-live, fig.asp = 0.5, fig.cap='Dynamic of leaf nitrogen concentration in Live pool for three components.'}
y_cols <- sprintf('Wheat.Leaf.Live.%sNConc', g_demand)
plot_report(g_report, g_xvar2, y_cols, x_lab = g_xlab2, 
            y_lab = expression(atop('Nitrogen concentration',
                                    '(g N '~g^-1~' biomass )')),
            y_labels = c(g_demand),
            ncol = 4)

```
</div>



<div class="fig-output">
```{r leaf-nitrogen-concentration-dead, fig.asp = 0.5, fig.cap='Dynamic of leaf nitrogen concentration in Dead pool for three components.'}
y_cols <- sprintf('Wheat.Leaf.Dead.%sNConc', g_demand)
plot_report(g_report, g_xvar2, y_cols, x_lab = g_xlab2, 
            y_lab = expression(atop('Nitrogen concentration',
                                    '(g N '~g^-1~' biomass )')),
            y_labels = g_demand,
            ncol = 4)

```
</div>





<div class="fig-output">
```{r leaf-nitrogen-sln, fig.asp = 1, fig.cap='Specific leaf nitrogen'}
y_cols <- c('Wheat.Leaf.SpecificLeafNitrogen')

plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Specific leaf nitrogen (g N'~m^-2~' leaf)'),
                               ncol = 3)
```
</div>
