## Demand {#sec:leaf-deman}

The leaf demand is summarised for all leaf cohorts in the expanding period (Figs \@ref(fig:leaf-life-cycle) and \@ref(fig:leaf-cohort-changing-no)), so that there is no leaf demand after `FlagLeaf`. No `Storage` demand is considered in the leaf organ. As the structural fraction is defined as `r get_fixed_value(g_pmf, 'Wheat.Leaf.StructuralFraction')`, the structural and metabolic demands have the same values in the whole life cycle. 

The daily demand ($D_{leaf}$) is the minimum between potential leaf area ($\Delta A_{p}$, Section \@ref(sec:leaf-potential-area)) and water stressed ($\Delta A_{w}$, Section \@ref(sec:leaf-water-area)) leaf area.

$$
D_{leaf} = \text{min} (\frac{\Delta A_{p}}{(\text{SLA}_{max} + \text{SLA}_{min}) / 2},\, \frac{\Delta A_{w}}{\text{SLA}_{min}})
$$

where, $\text{SLA}_{min}$ and $\text{SLA}_{max}$ are the minimum and maximum specific leaf areas, respectively (Fig. \@ref(fig:leaf-sla)). 


<div class="fig-output">
```{r leaf-demand, fig.asp = 1, fig.cap='Biomass demand by leaf. The structural and metabolic demands overlap each other as the structural fraction is defined as 0.5.'}
y_cols <- c('Wheat.Leaf.DMDemand.Structural',
            'Wheat.Leaf.DMDemand.Metabolic',
            'Wheat.Leaf.DMDemand.Storage')
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
        y_lab = expression('Demand (g biomass '~m^-2~' ground '~d^-1~')'),
            ncol = 3)

```
</div>

## Biomass dynamic {#sec:leaf-biomass}

<div class="fig-output">
```{r leaf-allocated, fig.asp = 1, fig.cap='Actual allocated biomass for leaf. The structural and metabolic weights overlap each other as the structural fraction is defined as 0.5.'}
y_cols <- c('Wheat.Leaf.Allocated.StructuralWt',
            'Wheat.Leaf.Allocated.MetabolicWt',
            'Wheat.Leaf.Allocated.StorageWt')
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Biomass (g biomass'~m^-2~' ground '~d^-1~')'),
            ncol = 3)
```
</div>




<div class="fig-output">
```{r leaf-weight, fig.asp = 1, fig.cap='Dynamic of leaf biomass (Total)'}
y_cols <- c('Wheat.LeafWt',
             'Wheat.Leaf.LiveWeight', 
             'Wheat.Leaf.DeadWeight')
y_labels <- c('Total', 'Live', 'Dead')
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Dry weight (g biomass'~m^-2~' ground)'),
            ncol = 3, y_labels = y_labels)

```
</div>



<div class="fig-output">
```{r leaf-live, fig.asp = 1, fig.cap='Dynamic of leaf biomass (Live component).'}
y_cols <- c('Wheat.Leaf.Live.StructuralWt',
            'Wheat.Leaf.Live.MetabolicWt',
            'Wheat.Leaf.Live.StorageWt')
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Dry weight (g biomass'~m^-2~' ground)'),
            ncol = 3,
            y_labels = c('Structural', "Metabolic", "Storage"))

```
</div>


<div class="fig-output">
```{r leaf-dead, fig.asp = 1, fig.cap='Dynamic of leaf biomass (Dead component).'}
y_cols <- c('Wheat.Leaf.Dead.StructuralWt',
            'Wheat.Leaf.Dead.MetabolicWt',
            'Wheat.Leaf.Dead.StorageWt')
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Biomass (g biomass' ~m^-2~' ground'), 
            ncol = 3,
            y_labels = c('Structural', "Metabolic", "Storage"))
```
</div>
