## Biomass supply {#sec:leaf-dm-supply}

In `Leaf` organ, the biomass supply only sources from `Fixation` (i.e. photosynthesis, Fig. \@ref(fig:leaf-dm-supply)). Three photosynthesis models are implemented in the APSIM next generation. 

```{r leaf-supply-config}
name_rue <- 'Wheat.Leaf.Photosynthesis_RUE'
```


### Radiation use efficiency model

The radiation-limited dry-biomass accumulation ($\Delta Q_{r}$) is calculated by the intercepted radiation ($I$), radiation use efficiency ($RUE$).

$$
\Delta Q_{r}=I \times RUE
$$

#### Radiation interception {-}

Radiation interception is calculated from the leaf area index (LAI, m$^{2}$ m$^{-2}$) and the extinction coefficient ($k$) [@MonsiFactorLightPlant2005]. 

$$
I=I_{0}(1-\exp(-k\times LAI)
$$


where $I_{0}$ is the total radiation at the top of the canopy (MJ) which is directly imported from weather records. Extinction coefficient ($k$) set as a constant value  `r get_fixed_value(g_pmf, 'Wheat.Leaf.ExtinctionCoeff')`.  


#### Actual radiation use efficiency {-}

The actual $RUE$ (g MJ$^{\text{-1}}$) is calculated as the potential $RUE$ ($RUE_p$) and several reduction factors, including plant nutrition ($F_{n,\ photo}$), air temperature($F_{t,\ photo}$), vapour pressure deficit ($F_{vpd}$), water supply ($F_w$) and atmospheric CO2 concentration ($F_{co2}$).

$$
RUE = RUE_{p} \times \min{(F_{t,\ photo}, F_{n,\ photo}, F_{VPD})} \times F_W \times F_{CO2}
$$

**The potential RUE ($RUE_p$)** has a default value `r get_fixed_value(g_pmf, paste0(name_rue, '.RUE'))`.

**The temperature factor ($F_t$)** is calculated as a function of average daily temperature weighted toward maximum temperature according to the specified `MaximumTemperatureWeighting` factor ($W_{maxt}$) with default value `r get_xml_value(g_pmf, '//RUEModel/WeightedTemperatureFunction/MaximumTemperatureWeighting')`.


$$
F_{t,\ photo}=h_{t,\ photo}[W_{maxt}T_{max}+(1-W_{maxt})T_{min}]
$$


<div class="fig-input">
```{r biomass-ft, fig.asp = 0.5, fig.cap='The temperature factor which influences radiation use efficiency'}
path <- paste0(name_rue, '.FT')
plot_xypair(g_pmf, path,
            x_lab = 'Average daily temperature weighted toward maximum temperature', 
            y_lab = 'Temperature factor to photosynthesis ([-])')
```
</div>


**The plant nutrition factor** is determined by the ratio of functional nitrogen in leaf (Fig. \@ref(fig:leaf-nitrogen-functional-n)) and the multiplier of nitrogen stress (Fig. \@ref(fig:leaf-rue-fn)).

<div class="fig-input">
```{r leaf-rue-fn, fig.asp = 0.5, fig.cap='The nitrogen factor which influences radiation use efficiency'}
path <- paste0(name_rue, '.FN')
plot_xypair(g_pmf, path, 
            x_lab = 'Ratio of functional nitrogen in leaf',
            y_lab = 'Nitrogen factor to photosynthesis ([-])')

```
</div>

**Water stress factor**

$F_{W}$ quantifies water stress and is calculated as <i>Leaf.Transpiration</i>/<i>Leaf.WaterDemand</i>, where <i>Leaf.Transpiration</i> is the minimum of <i>Leaf.WaterDemand</i> and <i>Root.WaterUptake</i>

<!--
Need to further check
-->

<div class="fig-input">
```{r leaf-rue-fw, fig.asp = 0.5, fig.cap='The water factor which influences radiation use efficiency'}
path <- paste0(name_rue, '.FW')
plot_xypair(g_pmf, path, x_lab = 'Water stress',
            y_lab = 'Water factor to photosynthesis ([-])')

```
</div>


**CO$_{\text{2}}$ factor** is calculated by a function of environmental CO$_{\text{2}}$ concentration ($C$, ppm; $C$ > 350 ppm) and daily mean temperature ($T_{mean}$ < 50&deg;C) as published by @ReyengaModellingglobalchange1999

$$
f_{c}=\frac{(C-C_{i})(350+2C_{i})}{(C+2C_{i})(350-C_{i})}
$$

where $C_{i}$ is the temperature dependent CO$_{\text{2}}$ compensation point (ppm) and is derived from the following function. 
$$
C_{i}=\frac{163-T_{mean}}{5-0.1T_{mean}}
$$



<div class="fig-input">
```{r leaf-supply-rue-co2, fig.asp=0.5, fig.cap="CO$_{2}$ factor in response to the CO$_{2}$ level for different mean air temperatures."}

    tmean <- seq(from = 0, to = 30, by = 10)
    co2 <- seq(350, 700, 10)
    tmean.len <- length(tmean)
    tmean <- rep(tmean, each = length(co2))
    co2 <- rep(co2, times = tmean.len)
    c1 <- (163 - tmean) / (5 - 0.1 * tmean)
    fc <- (co2 - c1) * (350 + 2 * c1) / ((co2 + 2 * c1) * (350 - c1))

    pd <- cbind(tmean = tmean, co2 = co2, fc = fc)
    pd <- as.data.frame(pd)

    key <- list(lines = list(col = 1:tmean.len,lty = 1:tmean.len),
                text = list(lab = as.character(seq(from = 0, to = 30, by = 10 ))),
                corner = c(0,1))

    ggplot(pd) +
        geom_line(aes(co2, fc, color = factor(tmean),
                      linetype = factor(tmean))) +
        theme_bw() +
        theme(legend.position = c(0.02, 0.98),
              legend.justification = c(0, 1)) +
        xlab('Carbon dioxide concentration (ppm)') +
        ylab(expression(~CO[2]~' factor for photosynthesis ([-])')) +
        guides(color = guide_legend(title = NULL),
               linetype = guide_legend(title = NULL))
```

</div>
### SPASS

### Layered Canopy Photosynthesis Model with Transpiration (or DCaPS)


### Comporison of three photosynthesis models

The daily photosynthesis is calculated by SPASS's model, but is exported for all three models to compare model performance. So the input parameters are the same for three models, e.g. leaf area index, temperature and radiation. 



<div class="fig-output">
```{r leaf-supply-all-models-radn, fig.asp = 1.2, fig.cap='Comparision of biomass supply from leaf using three photosynthesis models. The biomass supplies are directly exported from three models using the same inputs (e.g. leaf area index, radiation, temperature). The actual biomass supply is simuated by SPASS in the model.'}
y_cols <- c('Wheat.Leaf.Photosynthesis_RUE',
            'Wheat.Leaf.Photosynthesis_SPASS',
            'Wheat.Leaf.Photosynthesis_DCaPS')


p1 <- plot_report(g_report, 'Wheat.Phenology.DaysAfterSowing', y_cols, 
            x_lab = 'Days after sowing', 
             y_labels = c('RUE', 'SPASS', 'DCaPS'),
            y_lab = expression(atop('Gross photosynthesis rate', '(g biomass '~m^-2~' ground '~d^-1~')')), 
            ncol = 3) +
    geom_bar(aes(Wheat.Phenology.DaysAfterSowing, Weather.Radn),
             stat = 'identity', alpha = 0.7, width = 0.5,data = g_report) +
    scale_y_continuous(sec.axis = 
                           sec_axis(~., 
                                    name = expression('Radiation (MJ '~m^-2~')')))

p2 <- ggplot(g_report) +
    geom_bar(aes(Wheat.Phenology.DaysAfterSowing, Weather.MeanT),
             stat = 'identity', alpha = 0.7, width = 0.5, fill = 'black') +
    # ylab(expression(paste( "Daily mean temperature \n", ~"("*degree*"C)"))) +
    ylab(expression(atop("Daily mean temperature", "("*degree*"C)"))) +
    geom_line(aes(Wheat.Phenology.DaysAfterSowing, Wheat.Leaf.LAI * 5), color = 'blue') +
    scale_y_continuous(sec.axis = sec_axis(~./5, 
                                           name = expression('Leaf area index ('~m^2~' leaf '~m^-2~' ground)'),
                                           breaks = seq(1, 5),
                                           labels = paste0(' ', seq(1, 5)))) +
    theme_bw()

print(p1, vp = grid::viewport(0.5, 0.73, 1, 0.54))    
print(p2, vp = grid::viewport(0.5, 0.23, 1, 0.46))

```
</div>



<div class="fig-output">
```{r leaf-supply-all-model-lai, fig.asp = 0.5, fig.cap='Biomass supply of leaf using three photosynthesis models.'}
y_cols <- c('Wheat.Leaf.Photosynthesis_RUE',
            'Wheat.Leaf.Photosynthesis_SPASS',
            'Wheat.Leaf.Photosynthesis_DCaPS')


plot_report(g_report, 'Wheat.Leaf.LAI', y_cols, 
            y_labels = c('RUE', 'EW', 'DCaPS'),
            x_lab = expression('Leaf area index ('~m^2~" leaf "~m^-2~" ground)"), 
            y_lab = expression(atop('Gross photosynthesis rate', '(g biomass '~m^-2~' ground '~d^-1~')')),
            ncol = 3)

```
</div>


### Actual photosynthesis supply 

The actual gross photosynthesis supply is simulated by SPASS model.

<div class="fig-output">
```{r leaf-dm-supply, fig.asp = 1, fig.cap='Biomass supply from leaf'}
y_cols <- c('Wheat.Leaf.DMSupply.Fixation',
            'Wheat.Leaf.DMSupply.Retranslocation',
            'Wheat.Leaf.DMSupply.Reallocation')


plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression(atop('Gross photosynthesis rate', '(g biomass '~m^-2~' ground '~d^-1~')')),
            ncol = 3)

```
</div>

