# Grain {#cha:grain}

Grain is only the grain part of head.

```{r grain-setup, message=FALSE, warning=FALSE, echo=FALSE}
source('_script/setup.R')
```


## Grain number {#sec:grain-number}

Grain number is correlated with stem [ref] and/or spike [@SlaferGeneticimprovementeffectspreanthesis1990;@GonzalezPhotoperiodstemelongation2005] dry weight at anthesis.

The number of grains per plant ($N_{g}$) is determined by the `Stem` and `Spike` total biomass at `Flowering` (including `Live` and `Dead`).
$$
N_{g}=R_{g}(W_{stem} + W_{spike})
$$
where $W_{stem}$ and $W_{spike}$ are the stem and spkie total biomass at flowering, respectively. R_{g} is the grain number per gram stem and spike, with default value at `r get_fixed_value(g_pmf, 'Wheat.Grain.NumberFunction.GrainNumber.GrainsPerGramOfStem')` grain g<sup>-1</sup>.




## Biomass {#grain-biomass}

### Supply {#sec:grain-biomass-supply}

No biomass supply is considered in the `Grain` organ (Fig. \@ref(fig:grain-biomass-supply)).


<div class="fig-output">
```{r grain-biomass-supply, fig.asp = 0.5, fig.cap='Biomass supply from grain'}
y_cols <- c('Wheat.Grain.DMSupply.Fixation',
            'Wheat.Grain.DMSupply.Retranslocation',
            'Wheat.Grain.DMSupply.Reallocation')

plot_report(g_report, g_xvar2, y_cols, x_lab = g_xlab, 
            y_lab = expression(atop('Biomass supply', '(g biomass '~m^-2~' ground '~d^-1~')')), 
            ncol = 3)

```
</div>


### Demand {#sec:grain-biomass-demand}
The grain demand is seperated into two periods (i.e. from `Flowering` to `StartGrainFill` and from `StartGrainFill` to `EndGrainFill`). 


<div class="fig-output">
```{r grain-biomass-demand, fig.asp = 1, fig.cap='Biomass demand by grain'}
y_cols <- c('Wheat.Grain.DMDemand.Structural', 
            'Wheat.Grain.DMDemand.Metabolic', 
            'Wheat.Grain.DMDemand.Storage')
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Biomass demand (g biomass '~m^-2~' ground '~d^-1~')'), 
            ncol = 3)

```
</div>

### Actual allocation {#sec:grain-biomass-allocation}

`Grain` only considers the `Live` conponent, No `Dead` component.



<div class="fig-output">
```{r grain-biomass-allocated, fig.asp = 1, fig.cap='Actual allocated biomass for grain'}
y_cols <- c('Wheat.Grain.Allocated.StructuralWt',
            'Wheat.Grain.Allocated.MetabolicWt',
            'Wheat.Grain.Allocated.StorageWt')
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Allocated biomass (g biomass '~m^-2~' ground '~d^-1~')'),
            ncol = 3)
```
</div>




<div class="fig-output">
```{r grain-biomass-weight, fig.asp = 1, fig.cap='Dynamic of grain biomass (Total)'}
y_cols <- c('Wheat.GrainWt')

plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Biomass (g biomass '~m^-2~' ground '~d^-1~')'))

```
</div>





<div class="fig-output">
```{r grain-biomass-live, fig.asp = 1, fig.cap='Dynamic of grain biomass (Live component)'}
y_cols <- c('Wheat.Grain.Live.StructuralWt',
            'Wheat.Grain.Live.MetabolicWt',
            'Wheat.Grain.Live.StorageWt')

plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Biomass (g biomass '~m^-2~' ground '~d^-1~')'),
            ncol = 3)

```
</div>


<div class="fig-output">
```{r grain-biomass-dead, fig.asp = 0.5, fig.cap='Dynamic of grain biomass (Dead component)'}
y_cols <- c('Wheat.Grain.Dead.StructuralWt',
            'Wheat.Grain.Dead.MetabolicWt',
            'Wheat.Grain.Dead.StorageWt')


plot_report(g_report, g_xvar2, y_cols, x_lab = g_xlab, 
            y_lab = expression(atop('Biomass','(g biomass '~m^-2~' ground '~d^-1~')')),
            ncol = 3)

```
</div>




### Yield

The total grain weight at harvest can be considered as the final yield without moisture content in the grain. The normal range of moisture content in the grain is 10-15% with 12% as standard

<div class="fig-output">
```{r grain-biomass-yield, fig.asp = 0.5, fig.cap='Final yield with different moisture content.'}

final_yield <- max(g_report$Wheat.GrainWt)
mos <- seq(0, 15)
data_frame(Moisture = mos,
           yield = (1 + mos / 100) * final_yield / 100) %>% 
    ggplot() +
    geom_bar(aes(Moisture, yield), stat = 'identity', position = "dodge") +
    xlab('Moisture content (%)') + 
    ylab(expression('Yield (t'~ha^-1~')')) +
    theme_bw()
 
```
</div>

## Nitrogen {#sec:grain-nitrogen}


### Actual allocation {#sec:grain-nitrogen-allocated}



<div class="fig-output">
```{r grain-nitrogen-allocated, fig.asp = 1, fig.cap='Actual allocated nitrogen to grain for three components. The negative values of Storage indicate nitrogen is ratranslocated into other organs.'}
y_cols <- sprintf('Wheat.Grain.Allocated.%sN', g_demand)
            
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Allocated biomass (g biomass '~m^-2~' ground '~d^-1~')'),
            y_labels = g_demand, ncol = 3)


```
</div>



### Nitrogen contents {#sec:grain-nitrogen-contents}

<div class="fig-output">
```{r grain-nitrogen-wt, fig.asp = 1, fig.cap='Dynamic of grain nitrogen for three components.'}
y_cols <- sprintf('Wheat.Grain.%sN', g_demand)

plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Nitrogen contents (g N '~m^-2~' ground '~d^-1~')'),
            y_labels = g_demand,
            ncol = 4)

```
</div>




<div class="fig-output">
```{r grain-nitrogen-live, fig.asp = 1, fig.cap='Dynamic of grain nitrogen in Live pool for three components.'}
y_cols <- sprintf('Wheat.Grain.Live.%sN', g_demand)

plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Nitrogen contents (g N '~m^-2~' ground '~d^-1~')'),
             y_labels = g_demand,
            ncol = 4)

```
</div>



<div class="fig-output">
```{r grain-nitrogen-dead, fig.asp = 0.5, fig.cap='Dynamic of grain nitrogen in Dead pool for three components.'}
y_cols <- sprintf('Wheat.Grain.Dead.%sN', g_demand)

# Check all components equal to zero.
g_report %>% 
    select(y_cols) %>% 
    gather(trait, value, y_cols) %>% 
    group_by(trait) %>% 
    summarise(n = sum(value > 0)) %>% 
    filter(n > 0) %>% 
    ungroup() %>% 
    assertr::verify(nrow(.) == 0) %>% 
    invisible()
    
plot_report(g_report, g_xvar2, y_cols, x_lab = g_xlab2, 
            y_lab = expression('Nitrogen contents (g N '~m^-2~' ground '~d^-1~')'),
            y_labels = g_demand,
            ncol = 4)

```
</div>




### Nitrogen concentration {#sec:grain-nitrogen-conc}

<div class="fig-output">
```{r grain-nitrogen-concentration, fig.asp = 0.5, fig.cap='Dynamic of grain nitrogen concentration in Live and Dead.'}
y_cols <- c('Wheat.Grain.Live.NConc', 'Wheat.Grain.Dead.NConc',
            "Wheat.Grain.Nconc")

plot_report(g_report, g_xvar2, y_cols, x_lab = g_xlab2, 
            y_lab = expression(atop('Nitrogen concentration',
                                    '(g N '~g^-1~' biomass )')),
            y_labels = c("Live", "Dead", 'Whole grain'),
            ncol = 4)
```
</div>




<div class="fig-output">
```{r grain-nitrogen-concentration-live, fig.asp = 0.5, fig.cap='Dynamic of grain nitrogen concentration in Live pool for three components.'}
y_cols <- sprintf('Wheat.Grain.Live.%sNConc', g_demand)
plot_report(g_report, g_xvar2, y_cols, x_lab = g_xlab2, 
            y_lab = expression(atop('Nitrogen concentration',
                                    '(g N '~g^-1~' biomass )')),
            y_labels = c(g_demand),
            ncol = 4)

```
</div>



<div class="fig-output">
```{r grain-nitrogen-concentration-dead, fig.asp = 0.5, fig.cap='Dynamic of grain nitrogen concentration in Dead pool for three components.'}
y_cols <- sprintf('Wheat.Grain.Dead.%sNConc', g_demand)

plot_report(g_report, g_xvar2, y_cols, x_lab = g_xlab2, 
            y_lab = expression(atop('Nitrogen concentration',
                                    '(g N '~g^-1~' biomass )')),
            y_labels = g_demand,
            ncol = 4)

```
</div>



