# Root {#cha:root}


```{r root-setup, message=FALSE, warning=FALSE, echo=FALSE}
source('_script/setup.R')
```


Only `Structural` is considered in the three components of biomass for `Root`. The biomass allocation depending on the fraction of daily fixation (i.e. photosynthesis).


## Root Growth {#sec:root-growth}


### Root depth
```{r root-get-value}
s1 <- get_fixed_value(g_pmf,
      'Wheat.Root.RootFrontVelocity.PotentialRootFrontVelocity.PreEmergence.Value')
s2 <- get_fixed_value(g_pmf,
      'Wheat.Root.RootFrontVelocity.PotentialRootFrontVelocity.PostEmergence.Value')
```


Roots grow downwards through the soil profile, with initial depth determined by sowing depth and the growth rate determined by `RootFrontVelocity`, which is determined by potential root front velocity (`r s1` mm/d for pre emergencee, and `r s2` mm/d for post-emergence, Fig. \@ref(fig:root-front-velocity-potential)), and mofified (multification) by temperature (Fig. \@ref(fig:root-front-velocity-temp)) and water stress (Fig. \@ref(fig:root-front-velocity-water-stress)).

<div class="fig-input">
```{r root-front-velocity-potential, fig.asp = 0.5, fig.cap='The potential root front velocity.'}

v <- data_frame(stage = c(1, 3, 3, 9), velocity = c(s1, s1, s2, s2))

ggplot(v) +
    geom_path(aes(stage, velocity)) +
    theme_bw() +
    xlab('Stage') +
    ylab(expression('Potential root front velocity (mm '~d^-1~')')) +
    scale_x_continuous(breaks = seq(1, 9))

```
</div>




<div class="fig-input">
```{r root-front-velocity-temp, fig.asp = 0.5, fig.cap='The temperature stress on root front velocity.'}
path <- 'Wheat.Root.RootFrontVelocity.TemperatureFactor'
plot_xypair(g_pmf, path, 
            x_lab = expression('Daily mean temperature ('*degree*'C)'), 
            y_lab = 'Multiplier of root front velocity ([-])')
```
</div>



Soil water scale is A simple scale to convert soil water content into a value between 0 and 2 (i.e. from 0 to 1 when $SW$ is between $LL15$ and $DUL$ and from 1 to 2 when $SW$ is between $DUL$ and $SAT$, (Fig. \@ref(fig:root-front-velocity-waterscale))). 

<div class="fig-input">
```{r root-front-velocity-waterscale, fig.asp = 0.5, fig.cap='Response of soil water scale on soil water concentration in the top two layers of soil in the tested simulations.'}
dul <- get_soil_value(g_pmf, 'DUL')[1:2]
sat <- get_soil_value(g_pmf, 'SAT')[1:2]
ll15 <- get_soil_value(g_pmf, 'LL15')[1:2]

sw <- round(seq(min(ll15), 1, by = 0.01), 2)
wfd_all <- list()
for (i in seq(along = dul)) {
    wfd <- ifelse(sw > dul[i], 
                  pmax(1, pmin(2, 1 + (sw - dul[i]) / (sat[i] - dul[i]))),
                  pmax(0, pmin(1, (sw - ll15[i]) / (dul[i] - ll15[i])))
                  )    
    wfd_all[[i]] <- data_frame(layer = i, sw = sw, 
                               DUL = dul[i], SAT = sat[i], 
                               LL15 = ll15[i], wfd = wfd)
}
wfd_all <- bind_rows(wfd_all)
soil <- wfd_all %>% 
    select(-sw, -wfd) %>% 
    distinct() %>% 
    gather(trait, value, -layer) %>% 
    left_join(wfd_all %>% select(value = sw, wfd, layer),
              by = c('layer', "value"))
ggplot(wfd_all) +
    geom_line(aes(sw, wfd)) +
    geom_point(aes(x = value, y = wfd, color = trait), data = soil) +
    facet_wrap(~layer) +
    theme_bw() +
    xlab('Soil water concentration (%)') +
    ylab('Soil water scale ([-])') +
    theme(legend.position = 'bottom') +
    guides(color = guide_legend(title = NULL))

```
</div>


The multiplier of water stress on root front velocity depends on soil water scale which suppresses root growth when water scale is less than 0.25 (Fig. \@ref(fig:root-front-velocity-water-stress)). 


<div class="fig-input">
```{r root-front-velocity-water-stress, fig.asp = 0.5, fig.cap='Soil water stress on root front velocity'}
path <- c('Wheat.Root.RootFrontVelocity.WaterFactor')
plot_xypair(g_pmf, path, x_lab = 'Soil water scale ([-])', 
               y_lab = 'Multiplier of root front velocity ([-])')
```
</div>


<div class="fig-input">
```{r root-front-velocity, fig.asp = 1, fig.cap='Root front velocity.'}
y_cols <- c('Wheat.Root.RootFrontVelocity')
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Root front velocity (mm'~d^-1~')'))

```
</div>




<div class="fig-output">
```{r root-depth, fig.asp = 1, fig.cap='Root depth'}
y_cols <- c('Wheat.Root.Depth')
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = 'Root depth (mm)')

```
</div>


### Root length

Root length growth is calculated using the daily dry biomass partitioned to roots and a specific root length (`r get_fixed_value(g_pmf, 'Wheat.Root.SpecificRootLength')` m g^-1^ in default). Root proliferation in layers is calculated using an approach similar to the generalised equimarginal criterion used in economics.  The uptake of water and N per unit root length is used to partition new root material into layers of higher 'return on investment'.



<div class="fig-output">
```{r root-length, fig.asp = 1, fig.cap='Total root length'}

y_cols <- c('Wheat.Root.Length')
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = 'Root length (m)')

```
</div>






## Biomass {#sec:root-biomass}
### Supply {#sec:root-biomass-supply}

No biomass supply is considered in the `Root` organ (Fig. \@ref(fig:root-supply)).

<div class="fig-output">
```{r root-supply, fig.asp = 0.5, fig.cap='Biomass supply from root'}
y_cols <- c('Wheat.Root.DMSupply.Fixation',
            'Wheat.Root.DMSupply.Retranslocation',
            'Wheat.Root.DMSupply.Reallocation')

plot_report(g_report, g_xvar2, y_cols, x_lab = g_xlab2, 
            y_lab = expression(atop('Biomass supply', '(g biomass '~m^-2~' ground' ~d^-1~')')),
            ncol = 3)

```
</div>


### Demand {#sec:root-biomass-demand}

The daily biomass demand of `Root` is calculated as a fraction of daily fixation (i.e. photosynthesis) from Stage 3 (`Emergence`) to Stage 8 (`End of grain filling`). The fraction of root demand is 0.2 until `Flowering time`, then reduces into 0.02 until `End of grain filling` (Fig. \@ref(fig:root-demand-fraction)). Only structural demand is considered in the `Root` organ (Fig. \@ref(fig:root-demand)). 





<div class="fig-input">
```{r root-demand-fraction, fig.asp = 0.5, fig.cap='Fraction of root demand in the total fixation.'}
y_cols <- c('Wheat.Root.DMDemandFraction')
plot_report(g_report, g_xvar2, y_cols, x_lab = g_xlab2, 
            y_lab = 'Fraction of total fixation ([-])', ncol = 3)

```
</div>




<div class="fig-output">
```{r root-demand, fig.asp = 1, fig.cap='Biomass demand by root'}
y_cols <- c('Wheat.Root.DMDemand.Structural', 
            'Wheat.Root.DMDemand.Metabolic',
            'Wheat.Root.DMDemand.Storage')
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Biomass demand (g biomass'~m^-2~' ground '~d^-1~')'),
            ncol = 3)

```
</div>

### Biomass dynamic {#sec:root-biomass-dynamic}

The actual allocation (Fig. \@ref(fig:root-allocated)) is determined by the actual daily biomass supply (Fig. \@ref(fig:biomass-supply-total)) which may be smaller than than biomass demand (Fig. \@ref(fig:root-demand)). 

<div class="fig-output">
```{r root-allocated, fig.asp = 1, fig.cap='Actual allocated biomass for root'}
y_cols <- c('Wheat.Root.Allocated.StructuralWt',
            'Wheat.Root.Allocated.MetabolicWt',
            'Wheat.Root.Allocated.StorageWt')
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Allocated biomass (g biomass'~m^-2~' ground '~d^-1~')'),
            ncol = 3)
```
</div>

The daily loss of roots is calculated using a SenescenceRate function (0.005 in the default value).  All senescence material is automatically detached and added to the soil fresh organic matter (FOM) pool.  

<div class="fig-output">
```{r root-detached, fig.asp = 1, fig.cap='Detached biomass from root into soil organic.'}
y_cols <- c('Wheat.Root.Detached.StructuralWt', 
            'Wheat.Root.Detached.MetabolicWt',
            'Wheat.Root.Detached.StorageWt')
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Detached biomass (g biomass'~m^-2~' ground '~d^-1~')'), 
            ncol = 3)

```
</div>


Finally `Root` biomass increases until `flowering time`, then gradually decreases as the senescence is more than allocation (Fig. \@ref(fig:root-weight)). All biomass is allocated into `Live` component (Fig. \@ref(fig:root-live)), as the senescence `Root` immediately is detached and contributed into soil FOM (Fig. \@ref(fig:root-dead)).

<div class="fig-output">
```{r root-weight, fig.asp = 1, fig.cap='Dynamic of root biomass (Total)'}
y_cols <- c('Wheat.RootWt')
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Dry weight (g biomass'~m^-2~' ground)'), 
            ncol = 3)

```
</div>



<div class="fig-output">
```{r root-live, fig.asp = 1, fig.cap='Dynamic of root biomass (Live component)'}
y_cols <- c('Wheat.Root.Live.StructuralWt',
            'Wheat.Root.Live.MetabolicWt',
            'Wheat.Root.Live.StorageWt')
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Dry weight (g biomass'~m^-2~' ground)'),
            ncol = 3)

```
</div>


<div class="fig-output">
```{r root-dead, fig.asp = 0.5, fig.cap='Dynamic of root biomass (Dead component)'}
y_cols <- c('Wheat.Root.Dead.StructuralWt',
            'Wheat.Root.Dead.MetabolicWt',
            'Wheat.Root.Dead.StorageWt')
plot_report(g_report, g_xvar2, y_cols, x_lab = g_xlab2, 
            y_lab = expression('Dry weight (g biomass'~m^-2~' ground)'),
            ncol = 3)

```
</div>




## Nitrogen {#sec:root-nitrogen}


### Actual allocation {#sec:root-nitrogen-allocated}



<div class="fig-output">
```{r root-nitrogen-allocated, fig.asp = 1, fig.cap='Actual allocated nitrogen to root for three components. The negative values of Storage indicate nitrogen is ratranslocated into other organs.'}
y_cols <- sprintf('Wheat.Root.Allocated.%sN', g_demand)
            
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Allocated biomass (g biomass '~m^-2~' ground '~d^-1~')'),
            y_labels = g_demand, ncol = 3)

```
</div>


<div class="fig-output">
```{r root-nitrogen-detached, fig.asp = 0.5, fig.cap='Dynamic of root nitrogen in Detached pool for three components and total.'}
y_cols <- c(sprintf('Wheat.Root.Detached.%sN', g_demand), 'Wheat.Root.Detached.N')

plot_report(g_report, g_xvar2, y_cols, x_lab = g_xlab2, 
            y_lab = expression('Nitrogen contents (g N '~m^-2~' ground '~d^-1~')'),
             y_labels = c(g_demand, 'Total'),
            ncol = 4)

```
</div>



### Nitrogen contents {#sec:root-nitrogen-contents}

<div class="fig-output">
```{r root-nitrogen-wt, fig.asp = 1, fig.cap='Dynamic of root nitrogen for three components and total.'}
y_cols <- sprintf('Wheat.Root.%sN', g_demand)

plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Nitrogen contents (g N '~m^-2~' ground )'),
            y_labels = g_demand,
            ncol = 4)

```
</div>




<div class="fig-output">
```{r root-nitrogen-live, fig.asp = 1, fig.cap='Dynamic of root nitrogen in Live pool for three components and total.'}
y_cols <- sprintf('Wheat.Root.Live.%sN', g_demand)

plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Nitrogen contents (g N '~m^-2~' ground)'),
            y_labels = g_demand,
            ncol = 4)

```
</div>



<div class="fig-output">
```{r root-nitrogen-dead, fig.asp = 0.5, fig.cap='Dynamic of root nitrogen in Dead pool for three components and total.'}
y_cols <- sprintf('Wheat.Root.Dead.%sN', g_demand)

# Check all components equal to zero.
g_report %>% 
    select(y_cols) %>% 
    gather(trait, value, y_cols) %>% 
    group_by(trait) %>% 
    summarise(n = sum(value > 0)) %>% 
    filter(n > 0) %>% 
    ungroup() %>% 
    assertr::verify(nrow(.) == 0) %>% 
    invisible()
    
plot_report(g_report, g_xvar2, y_cols, x_lab = g_xlab2, 
            y_lab = expression('Nitrogen contents (g N '~m^-2~' ground)'),
            y_labels = g_demand,
            ncol = 4)

```
</div>




### Nitrogen concentration {#sec:root-nitrogen-conc}

<div class="fig-output">
```{r root-nitrogen-concentration, fig.asp = 0.5, fig.cap='Dynamic of root nitrogen concentration in Live and Dead.'}
y_cols <- c('Wheat.Root.Live.NConc', 'Wheat.Root.Dead.NConc',
            "Wheat.Root.Nconc")

plot_report(g_report, g_xvar2, y_cols, x_lab = g_xlab2, 
            y_lab = expression(atop('Nitrogen concentration',
                                    '(g N '~g^-1~' biomass )')),
            y_labels = c("Live", "Dead", 'Whole root'),
            ncol = 4)
```
</div>




<div class="fig-output">
```{r root-nitrogen-concentration-live, fig.asp = 0.5, fig.cap='Dynamic of root nitrogen concentration in Live pool for three components and total.'}
y_cols <- sprintf('Wheat.Root.Live.%sNConc', g_demand)

plot_report(g_report, g_xvar2, y_cols, x_lab = g_xlab2, 
            y_lab = expression(atop('Nitrogen concentration',
                                    '(g N '~g^-1~' biomass )')),
            y_labels = g_demand,
            ncol = 4)

```
</div>



<div class="fig-output">
```{r root-nitrogen-concentration-dead, fig.asp = 0.5, fig.cap='Dynamic of root nitrogen concentration in Dead pool for three components and total.'}
y_cols <- sprintf('Wheat.Root.Dead.%sNConc', g_demand)

plot_report(g_report, g_xvar2, y_cols, x_lab = g_xlab2, 
            y_lab = expression(atop('Nitrogen concentration',
                                    '(g N '~g^-1~' biomass )')),
            y_labels = g_demand,
            ncol = 4)

```
</div>


