# Spike {#cha:spike}


```{r spike-setup, message=FALSE, warning=FALSE, echo=FALSE}
source('_script/setup.R')
```

```{r spike-biomass-parameter}
spike_max_weight <- get_fixed_value(g_pmf, 'Wheat.Spike.DMDemandFunction.MaximumOrganWt')
spike_duration <- max(g_report$Wheat.Spike.DMDemandFraction.GrowthDuration)
spike_structure_fraction <- get_fixed_value(g_pmf, 'Wheat.Spike.StructuralFraction')
spike_max_weight2 <- round(spike_max_weight * spike_structure_fraction, 2)
spike_number <- g_report$Wheat.Structure.TotalStemPopn[nrow(g_report)]
spike_max_weight_p <- round(spike_number * spike_max_weight2)
spike_growth_rate_p <- round(spike_max_weight_p / spike_duration, 2)
spike_retranslocation <- get_fixed_value(g_pmf, 'Wheat.Spike.DMRetranslocationFactor.ReproductiveGrowth.DMRetranslocationFactor')

```


Spike is the head parts without grain including pedicel and glunes. `Spike` provides biomass through retranslocation, requires biomass depending on the population and potential spike weight. The biomass is allocated into two components, i..e `Structural` and `Storage`. No `Metabolic` is considered.

## Biomass {#sec:spike-biomass}

### Supply {#sec:spike-dm-supply}

In `Spike`, the biomass supply only sources from retranslocation (Fig. \@ref(fig:spike-dm-supply)). Daily retranslocation is the proportion of current storage ($B_{spike, storage}$) from `StartGrainFill` to `EndGrainFill` with default value `r spike_retranslocation`, i.e. daily retranslocatable biomass is `r spike_retranslocation * 100`% of total storage during grain filling (Fig. \@ref(fig:spike-dm-retran-factor)).


<div class="fig-input">
```{r spike-dm-retran-factor, fig.asp = 0.5, fig.cap='Growth duration of spike development'}

y_cols <- c('Wheat.Spike.DMRetranslocationFactor')
g_report %>% 
    # filter(Wheat.Phenology.Stage > 5) %>% 
    plot_report(g_xvar2, y_cols, x_lab = g_xlab,
            y_lab = 'Factor of retranslocation ([-])')
```
</div>



<div class="fig-output">
```{r spike-dm-supply, fig.asp = 1, fig.cap='Biomass supply from spike'}
y_cols <- c('Wheat.Spike.DMSupply.Fixation',
            'Wheat.Spike.DMSupply.Retranslocation',
            'Wheat.Spike.DMSupply.Reallocation')

plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Biomass supply (g biomamss '~m^-2~" ground "~d^-1~')'),
            ncol = 3)

```
</div>


### Demand {#spike-dm-demand}



The biomass demand is calculated as the total demands of two components (i.e. structural $BD_{spike,\,structural}$ and storage $BD_{spike,\,storage}$) as no metabolic demand is considered in the wheat model. The structural fraction $F_{spike, structure}$ is defined as the fraction of structural component as total biomass (`r spike_structure_fraction`), i.e. $1-F_{spike, structure}$ is the fraction of storage biomass.  

The spike demand depends on the the potential weight of a spike ($B_{max, spike}$) and head number ($N_{head}$) during spike growth period. In theory, $B_{max, spike}$ contains the structural and metabolic components (`r spike_max_weight` g per spike in default value). However, no metabolic component is considered in spike. The potential weight of a spike is `r spike_max_weight2` g per spike and `r spike_max_weight_p` g m^-2^ in the population only for structural component.


**Structural demand** of `Spike` ($BD_{spike, structural}$) is determined by the population based demand function since Stage 5 (`FlagLeaf`) to Stage 7 (`StartGrainFill`). The structural demand includes the growth respiration (Section \@ref(sec:biomass-respiration-growth)). 

$$
BD_{spike, structural} = \Delta TT \times N_{head} \frac {B_{max, spike}}{T_{growth}} \times F_{spike, structure} / C_{spike, efficiency}
$$
where $\Delta TT$ is the daily thermal time in the phenology module (Fig. \@ref(fig:phenology-tt)); $N_{head}$ is the head number per unit area ( # m^-2^ ground), i.e. total stem population at flowering time (Fig. \@ref(fig:str-live-stem-number)); $W_{max, spike}$ is the potential weight of spike (`r spike_max_weight` g per spike). $T_{growth}$ is the growth duration of spike ($TT$, the thermal time target from `FlagLeaf` to `StartGrainFill`). As the target of `EarlyReproductive` is sensitive to photoperiod (Section \@ref(sec:phe-stage-period)), the growth duration can be changed during spike development depending on the photoperiod (Fig. \@ref(fig:spike-growth-duration)). Consequently, the potential growth rate is `r spike_growth_rate_p` g m^-2^ ground &deg;Cd^-2^.

$F_{spike, structure}$ is the structural fraction of `Spike` with default value `r get_fixed_value(g_pmf, 'Wheat.Spike.StructuralFraction')`. $C_{spike,efficiency}$ is the conversion efficiency of `Spike`, i.e. the efficiency of allocation biomass converted into carbon (growth respiration). $C_{efficiency}$ has the default value `r get_fixed_value(g_pmf, 'Wheat.Spike.DMConversionEfficiency')` and is counted before allocation. 


<div class="fig-output">
```{r spike-number, fig.asp = 1, fig.cap='Head, live stem and total population in unit area. The head number is determined at flag leaf stage as the total stem population.'}
y_cols <- c('Wheat.Spike.HeadNumber',
            'Wheat.Leaf.LiveStemNumber',
            'Wheat.Structure.TotalStemPopn')
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Number (#'~m^-2~' ground )'),
            ncol = 3)
```
</div>


<div class="fig-input">
```{r spike-growth-duration, fig.asp = 0.5, fig.cap='Growth duration of spike development'}
y_cols <- c('Wheat.Spike.DMDemandFraction.GrowthDuration')
g_report %>% 
    filter(Wheat.Phenology.Stage > 5) %>% 
    plot_report(g_xvar2, y_cols, x_lab = g_xlab2,
            y_lab = expression('Growth duration ('*degree*'Cd)'))
```
</div>


**Storage demand** ($BD_{spike,\,storage}$) is to fill the non-structural components (i.e. storage for `Spike`) as the difference of theoretical maximum and base allocated biomass, and then divides growth respiration (Section \@ref(sec:biomass-respiration-growth)). 

$$
BD_{spike,\,storage} = [\frac{B_{spike,\,structural} + BD_{spike,\,structural}}{F_{spike, structure}} - (B_{spike} + BD_{spike,\,structural})] / C_{spike, efficiency}
$$

The theoretical maximum biomass equals to current spike structural weight ($B_{spike,\,structural}$) plus structural demand ($BD_{spike,\,structural}$), then divide the structural fraction ($F_{spike, structure}$). The base allocated biomass equals to current spike weight ($B_{spike}$) plus structural demand ($BD_{spike,\,structural}$). 

Consequently, the spike grows from `FlagLeaf` to `StartGrainFill`, and can store more biomass until maturity (Fig. \@ref(fig:spike-dm-demand)). The actual growth rate of spike depends on the potential size and daily thermal time. 

<div class="fig-output">
```{r spike-dm-demand, fig.asp = 1, fig.cap='Biomass demand by spike'}
y_cols <- c('Wheat.Spike.DMDemand.Structural',
            'Wheat.Spike.DMDemand.Metabolic',
            'Wheat.Spike.DMDemand.Storage')
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Demand (g biomass'~m^-2~' ground ' ~d^-1~')'),
            ncol = 3)
```
</div>


### Actual allocation {#spike-dm-allocation}

The actual allocation is constrained by the nitrogen allocation. 


The actual allocation reflects the increase of structural component, and retranslocation of storage component (Fig. \@ref(fig:spike-dm-allocated)). `Spike` only considers the `Live` biomass (Fig. \@ref(fig:spike-dm-live)), no `Dead` biomass (Fig. \@ref(fig:spike-dm-dead)).


<div class="fig-output">
```{r spike-dm-allocated, fig.asp = 1, fig.cap='Actual allocated biomass to spike for three components. The negative values of Storage indicate biomass is ratranslocated into other organs.'}
y_cols <- c('Wheat.Spike.Allocated.StructuralWt',
            'Wheat.Spike.Allocated.MetabolicWt',
            'Wheat.Spike.Allocated.StorageWt')
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Allocated biomass (g biomass '~m^-2~" ground "~d^-1~')'), 
            ncol = 3)

```
</div>



<div class="fig-output">
```{r spike-dm-weight, fig.asp = 1, fig.cap='Dynamic of spike dry weights for three components and total.'}
y_cols <- c(sprintf('Wheat.Spike.%sWt', g_demand), 'Wheat.SpikeWt')
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Dry weight (g biomass '~m^-2~' ground '~d^-1~')'),
            y_labels = c(g_demand, 'Total'),
            ncol = 4)

```
</div>



<div class="fig-output">
```{r spike-dm-live, fig.asp = 1, fig.cap='Dynamic of spike biomass in Live pool for three components and total.'}
y_cols <- c(sprintf('Wheat.Spike.Live.%sWt', g_demand), 'Wheat.Spike.LiveWt')
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Dry weight (g biomass '~m^-2~' ground '~d^-1~')'),
             y_labels = c(g_demand, 'Total'),
            ncol = 4)
```
</div>

<div class="fig-output">
```{r spike-dm-dead, fig.asp = 1, fig.cap='Dynamic of spike biomass in Dead pool for three components and total.'}
y_cols <- c(sprintf('Wheat.Spike.Dead.%sWt', g_demand), 'Wheat.Spike.DeadWt')

# Check all components equal to zero.
g_report %>% 
    select(y_cols) %>% 
    gather(trait, value, y_cols) %>% 
    group_by(trait) %>% 
    summarise(n = sum(value > 0)) %>% 
    filter(n > 0) %>% 
    ungroup() %>% 
    assertr::verify(nrow(.) == 0) %>% 
    invisible()
    
plot_report(g_report, g_xvar, y_cols, x_lab = g_xlab, 
            y_lab = expression('Dry weight (g biomass '~m^-2~' ground '~d^-1~')'),
             y_labels = c(g_demand, 'Total'),
            ncol = 4)
```
</div>



## Nitrogen {#sec:spike-nitrogen}

